---
title: "Review_Simi_260501"
author: "Samxie"
date: "2026-05-01"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)
```

```{r packages}
library(dplyr)
library(readr)
library(stringr)
library(lubridate)
library(tidyr)
library(haven)
library(purrr)
```

## 0. Notes

本版脚本只做以下事情：

1. `simi` 直接从已经保存好的面板读取（不再计算 month + before 评论拼接）。
2. 重新构建并扩展 `revenue_comp`（zip / city 多算法）。
3. 增加一批动态变量（尤其是 `d_sim_mean`、竞争强度、相对 RevPAR、前瞻变量）。
4. 固定 `winsor_city_1_99`，只沿评论总量阈值重建同样本主样本，并导出 `260407` 结果口径。
5. 给出可直接在 R 里复现的同样本 level `FE` / `OLS`、`City×Year×Mon demean FE/OLS` 与核心异质性结果。

当前口径说明：

5. 现有 `sim_mean` 先统一视为当前 `10` 口径的 `ARS`。
6. 本版暂不重建 `15 / 20 / 30`、`rolling similarity`、`JSD` 等 alternative `ARS`。
7. `FE` 是主结果，`OLS` 与后续 `sys-GMM` 只作为同一样本定义下的稳健性。

```{r path}
detect_project_dir <- function() {
  input <- tryCatch(knitr::current_input(), error = function(e) NULL)
  if (!is.null(input) && nzchar(input)) {
    input_dir <- dirname(normalizePath(input, winslash = "/", mustWork = FALSE))
    if (dir.exists(file.path(input_dir, "raw_inputs"))) {
      return(normalizePath(input_dir, winslash = "/", mustWork = TRUE))
    }
  }
  cwd <- normalizePath(getwd(), winslash = "/", mustWork = TRUE)
  if (dir.exists(file.path(cwd, "raw_inputs"))) return(cwd)
  stop("Cannot locate sharing folder. Run/knit this Rmd from the folder containing raw_inputs/.")
}

project_dir <- detect_project_dir()
raw_dir <- file.path(project_dir, "raw_inputs")
path_panel_in <- file.path(raw_dir, "valid_match_review_acc_10_zip.dta")
path_revenue_bind <- file.path(raw_dir, "revenue_tp_all_bind0123Zip.csv")
path_star_lookup <- file.path(raw_dir, "data_tax_trip_month.csv")
output_root <- project_dir
data_dir <- project_dir
csv_dir <- file.path(project_dir, "csv")
scan_dir <- file.path(project_dir, "scans")

for (dir_path in c(csv_dir, scan_dir)) {
  dir.create(dir_path, recursive = TRUE, showWarnings = FALSE)
}

path_out_panel_main <- file.path(data_dir, "valid_match_review_acc_260407_main.dta")
path_out_hotel_review <- file.path(data_dir, "hotel_review_total_260325.dta")
path_out_sample_audit <- file.path(csv_dir, "sample_audit_260407.csv")
path_out_sample_rule_scan <- file.path(scan_dir, "sample_rule_scan_260407.csv")
path_out_sample_review_focus_scan <- file.path(scan_dir, "sample_review_focus_scan_260407.csv")
path_out_sample_control_scan <- file.path(scan_dir, "sample_control_scan_260407.csv")
path_out_main_effect <- file.path(csv_dir, "main_effect_260407.csv")
path_out_main_effect_demean_scan <- file.path(scan_dir, "main_effect_demean_scan_260407.csv")
path_out_hetero_core <- file.path(csv_dir, "heterogeneity_core_260407.csv")
path_out_hetero_rule_scan <- file.path(scan_dir, "heterogeneity_rule_scan_260407.csv")
path_out_hetero_threshold_scan <- file.path(scan_dir, "heterogeneity_threshold_scan_260407.csv")
path_out_hetero_control_scan <- file.path(scan_dir, "heterogeneity_control_scan_260407.csv")
path_out_hetero_diff_tests <- file.path(csv_dir, "heterogeneity_diff_tests_260407.csv")
path_out_hetero_interaction <- file.path(csv_dir, "heterogeneity_interaction_260407.csv")
path_out_hetero_interaction_scan <- file.path(scan_dir, "heterogeneity_interaction_scan_260407.csv")
path_out_star_coverage <- file.path(csv_dir, "star_coverage_260407.csv")
```

```{r tuning}
current_ars_window <- 10L
candidate_revenue_rules <- "winsor_city_1_99"
candidate_focus_thresholds_primary <- c(80L, 100L, 120L, 150L, 200L, 300L)
candidate_focus_thresholds_secondary <- c(110L, 130L, 140L)
candidate_focus_thresholds <- candidate_focus_thresholds_primary
main_sample_min_n <- 24000L
main_sample_min_hotels <- 400L
baseline_min_obs <- 30316L
baseline_min_hotels <- 474L
group_min_n <- 1000L
perm_reps_base <- 1000L
perm_reps_refine <- 5000L
audit_sig_cutoff <- 0.05
screen_sig_cutoff <- 0.05
```

## 1. Load Existing Panel (Directly Use Saved Simi)

```{r read-panel}
panel_raw <- read_dta(path_panel_in) %>%
  mutate(
    HotelID = as.character(HotelID),
    CityID = as.character(CityID),
    year_month = sprintf("%04d-%02d", Year, Mon),
    ym_date = as.Date(sprintf("%04d-%02d-01", Year, Mon))
  ) %>%
  arrange(HotelID, Year, Mon)

review_total_hotel <- panel_raw %>%
  group_by(HotelID) %>%
  summarize(review_total_hotel = max(volumn_acc, na.rm = TRUE), .groups = "drop")

panel_raw %>%
  summarize(
    n_obs = n(),
    n_hotel = n_distinct(HotelID),
    sim_na = mean(is.na(sim_mean)),
    lag_sim_na = mean(is.na(lag_sim_mean))
  )
```

## 2. Rebuild Competitor Revenue Variables (Multiple Algorithms)

### 2.1 Revenue Universe

```{r read-revenue}
revenue_bind <- read_csv(path_revenue_bind, show_col_types = FALSE) %>%
  mutate(
    HotelID = as.character(HotelID),
    CityID = as.character(CityID),
    Zip = as.character(Zip)
  ) %>%
  distinct(HotelID, Year, Mon, .keep_all = TRUE) %>%
  left_join(review_total_hotel, by = "HotelID") %>%
  filter(!is.na(RevPAR), RevPAR > 0)

sample_hotels <- unique(panel_raw$HotelID)
revenue_sample <- revenue_bind %>% filter(HotelID %in% sample_hotels)
revenue_review_filtered <- revenue_bind %>%
  filter(review_total_hotel >= min(candidate_focus_thresholds))
```

### 2.2 Helper: Group-Level Competition Stats

```{r helper-func}
winsor_by_group <- function(data, value, group, p = c(0.01, 0.99), suffix = "_w199") {
  value_quo <- rlang::enquo(value)
  group_quo <- rlang::enquo(group)
  value_nm <- rlang::as_name(value_quo)
  new_nm <- paste0(value_nm, suffix)

  data %>%
    group_by(!!group_quo) %>%
    mutate(
      q_lo_tmp = quantile(!!value_quo, p[1], na.rm = TRUE),
      q_hi_tmp = quantile(!!value_quo, p[2], na.rm = TRUE),
      !!new_nm := pmin(pmax(!!value_quo, q_lo_tmp), q_hi_tmp)
    ) %>%
    ungroup() %>%
    select(-q_lo_tmp, -q_hi_tmp)
}

build_comp_metrics <- function(df, scope_name = "full") {
  zip_grp <- df %>%
    group_by(Zip, Year, Mon) %>%
    summarize(
      zip_n = n(),
      zip_sum = sum(RevPAR, na.rm = TRUE),
      zip_mean = mean(RevPAR, na.rm = TRUE),
      zip_median = median(RevPAR, na.rm = TRUE),
      zip_sd = sd(RevPAR, na.rm = TRUE),
      zip_trim10 = mean(RevPAR[RevPAR >= quantile(RevPAR, 0.1, na.rm = TRUE) &
                                 RevPAR <= quantile(RevPAR, 0.9, na.rm = TRUE)], na.rm = TRUE),
      .groups = "drop"
    )

  city_grp <- df %>%
    group_by(CityID, Year, Mon) %>%
    summarize(
      city_n = n(),
      city_sum = sum(RevPAR, na.rm = TRUE),
      city_mean = mean(RevPAR, na.rm = TRUE),
      city_median = median(RevPAR, na.rm = TRUE),
      city_sd = sd(RevPAR, na.rm = TRUE),
      city_trim10 = mean(RevPAR[RevPAR >= quantile(RevPAR, 0.1, na.rm = TRUE) &
                                  RevPAR <= quantile(RevPAR, 0.9, na.rm = TRUE)], na.rm = TRUE),
      .groups = "drop"
    )

  out <- df %>%
    left_join(zip_grp, by = c("Zip", "Year", "Mon")) %>%
    left_join(city_grp, by = c("CityID", "Year", "Mon")) %>%
    mutate(
      comp_zip_mean_excl = if_else(zip_n > 1, (zip_sum - RevPAR) / (zip_n - 1), NA_real_),
      comp_city_mean_excl = if_else(city_n > 1, (city_sum - RevPAR) / (city_n - 1), NA_real_),
      high_comp_zip = as.integer(zip_n >= 5),
      high_comp_city = as.integer(city_n >= 20)
    ) %>%
    select(
      HotelID, Year, Mon, Zip, CityID, RevPAR,
      zip_n, city_n, high_comp_zip, high_comp_city,
      comp_zip_mean_excl, zip_mean, zip_median, zip_trim10, zip_sd,
      comp_city_mean_excl, city_mean, city_median, city_trim10, city_sd
    )

  names(out) <- names(out) %>%
    str_replace("^zip_n$", paste0("zip_n_", scope_name)) %>%
    str_replace("^city_n$", paste0("city_n_", scope_name)) %>%
    str_replace("^high_comp_zip$", paste0("high_comp_zip_", scope_name)) %>%
    str_replace("^high_comp_city$", paste0("high_comp_city_", scope_name)) %>%
    str_replace("^comp_zip_mean_excl$", paste0("comp_zip_mean_excl_", scope_name)) %>%
    str_replace("^zip_mean$", paste0("zip_mean_", scope_name)) %>%
    str_replace("^zip_median$", paste0("zip_median_", scope_name)) %>%
    str_replace("^zip_trim10$", paste0("zip_trim10_", scope_name)) %>%
    str_replace("^zip_sd$", paste0("zip_sd_", scope_name)) %>%
    str_replace("^comp_city_mean_excl$", paste0("comp_city_mean_excl_", scope_name)) %>%
    str_replace("^city_mean$", paste0("city_mean_", scope_name)) %>%
    str_replace("^city_median$", paste0("city_median_", scope_name)) %>%
    str_replace("^city_trim10$", paste0("city_trim10_", scope_name)) %>%
    str_replace("^city_sd$", paste0("city_sd_", scope_name))

  out
}
```

### 2.3 Build Full-Universe and Sample-Only Competition Metrics

```{r comp-build}
comp_full <- build_comp_metrics(revenue_bind, scope_name = "full")
comp_sample <- build_comp_metrics(revenue_sample, scope_name = "sample")
comp_review <- build_comp_metrics(revenue_review_filtered, scope_name = "review")
```

## 3. Merge and Build New Variables

```{r merge-build}
panel_model <- panel_raw %>%
  left_join(review_total_hotel, by = "HotelID") %>%
  left_join(
    comp_full %>% select(-RevPAR, -CityID),
    by = c("HotelID", "Year", "Mon")
  ) %>%
  left_join(
    comp_sample %>% select(-RevPAR, -CityID, -Zip),
    by = c("HotelID", "Year", "Mon")
  ) %>%
  left_join(
    comp_review %>% select(-RevPAR, -CityID, -Zip),
    by = c("HotelID", "Year", "Mon")
  ) %>%
  arrange(HotelID, Year, Mon) %>%
  group_by(HotelID) %>%
  mutate(
    ln_RevPAR = if_else(RevPAR > 0, log(RevPAR), NA_real_),
    ln_lag_RevPAR = if_else(lag_RevPAR > 0, log(lag_RevPAR), NA_real_),
    ln_recent_volumn = if_else(recent_volumn > 0, log(recent_volumn), NA_real_),
    ln_lag_volumn_acc = if_else(lag_volumn_acc >= 0, log(lag_volumn_acc + 1), NA_real_),
    ln_avg_com_RevPAR = if_else(avg_com_RevPAR > 0, log(avg_com_RevPAR), NA_real_),
    ln_lag_avg_com_RevPAR = if_else(lag_avg_com_RevPAR > 0, log(lag_avg_com_RevPAR), NA_real_),

    # 重点动态变量：比 level 更接近“变化冲击”
    d_sim_mean = sim_mean - lag_sim_mean,
    d_ln_RevPAR = ln_RevPAR - ln_lag_RevPAR,
    lag2_sim_mean = lag(sim_mean, 2),
    lag3_sim_mean = lag(sim_mean, 3),

    # 评论机制补充变量
    rating_momentum = lag_avg_rating_month - lag_avg_rating_acc,
    rating_recent_gap = lag_rating_last_5 - lag_avg_rating_month,
    volume_momentum = ln_recent_volumn - log(lag_recent_volumn + 1),
    review_freshness = lag_recent_volumn / (lag_volumn_acc + 1),

    sim_mean_std_hotel = as.numeric(scale(sim_mean)),
    sim_high_p90_hotel = as.integer(sim_mean >= quantile(sim_mean, 0.9, na.rm = TRUE))
  ) %>%
  ungroup()
```

### 3.1 Merge Legacy Star Class

```{r merge-star}
star_lookup <- read_csv(
  path_star_lookup,
  show_col_types = FALSE,
  col_types = cols(.default = col_character())
) %>%
  transmute(
    HotelID = as.character(HotelID),
    star_class = suppressWarnings(as.numeric(StarClass))
  ) %>%
  filter(HotelID != "", !is.na(star_class)) %>%
  distinct(HotelID, .keep_all = TRUE)

panel_model <- panel_model %>%
  left_join(star_lookup, by = "HotelID") %>%
  mutate(
    star_ge3 = case_when(
      is.na(star_class) ~ NA_integer_,
      star_class >= 3 ~ 1L,
      TRUE ~ 0L
    )
  )
```

### 3.2 Log and Gap Variables for Multiple Competitor Algorithms

```{r comp-log-gap}
comp_var_candidates <- c(
  "comp_zip_mean_excl_full", "zip_mean_full", "zip_median_full", "zip_trim10_full",
  "comp_city_mean_excl_full", "city_mean_full", "city_median_full", "city_trim10_full",
  "comp_zip_mean_excl_sample", "zip_mean_sample", "zip_median_sample", "zip_trim10_sample",
  "comp_city_mean_excl_sample", "city_mean_sample", "city_median_sample", "city_trim10_sample",
  "comp_zip_mean_excl_review", "zip_mean_review", "zip_median_review", "zip_trim10_review",
  "comp_city_mean_excl_review", "city_mean_review", "city_median_review", "city_trim10_review"
)

comp_var_candidates <- comp_var_candidates[comp_var_candidates %in% names(panel_model)]

for (v in comp_var_candidates) {
  ln_name <- paste0("ln_", v)
  panel_model[[ln_name]] <- ifelse(panel_model[[v]] > 0, log(panel_model[[v]]), NA_real_)
}

panel_model <- panel_model %>%
  mutate(
    gap_zip_mean_full = ln_RevPAR - ln_comp_zip_mean_excl_full,
    gap_city_mean_full = ln_RevPAR - ln_comp_city_mean_excl_full,
    gap_zip_median_full = ln_RevPAR - ln_zip_median_full,
    gap_city_median_full = ln_RevPAR - ln_city_median_full,
    gap_zip_mean_review = ln_RevPAR - ln_comp_zip_mean_excl_review,
    gap_city_mean_review = ln_RevPAR - ln_comp_city_mean_excl_review
  )
```

### 3.3 City-Month Median Split Variables (Fix Do-File Typo)

```{r split-vars}
panel_model <- panel_model %>%
  group_by(CityID, year_month) %>%
  mutate(
    median_ratingacc = median(lag_avg_rating_acc, na.rm = TRUE),
    median_volume_acc = median(lag_volumn_acc, na.rm = TRUE),
    median_sd_acc = median(lag_sd_acc, na.rm = TRUE),
    median_lag_avg_rating_month = median(lag_avg_rating_month, na.rm = TRUE),
    median_lag_recent_volumn = median(lag_recent_volumn, na.rm = TRUE),
    median_recent_volumn = median(recent_volumn, na.rm = TRUE),
    high_rating_acc = as.integer(lag_avg_rating_acc >= median_ratingacc),
    # 这里修正：应该用 lag_avg_rating_month，而不是 lag_avg_rating_acc
    high_rating_month = as.integer(lag_avg_rating_month >= median_lag_avg_rating_month),
    high_sd_acc = as.integer(lag_sd_acc >= median_sd_acc),
    high_volume_acc = as.integer(lag_volumn_acc >= median_volume_acc),
    high_volume_month = as.integer(lag_recent_volumn >= median_lag_recent_volumn),
    high_recent_volumn = as.integer(recent_volumn >= median_recent_volumn)
  ) %>%
  ungroup()
```

### 3.4 Winsorize (By CityID) and Final Transform

```{r winsor}
panel_model <- panel_model %>%
  winsor_by_group(RevPAR, CityID, p = c(0.01, 0.99), suffix = "_w199") %>%
  winsor_by_group(lag_RevPAR, CityID, p = c(0.01, 0.99), suffix = "_w199") %>%
  winsor_by_group(sim_mean, HotelID, p = c(0.01, 0.99), suffix = "_w199") %>%
  group_by(HotelID) %>%
  arrange(Year, Mon, .by_group = TRUE) %>%
  mutate(
    lag_sim_mean_w199 = lag(sim_mean_w199),
    d_sim_mean_w199 = sim_mean_w199 - lag_sim_mean_w199
  ) %>%
  ungroup() %>%
  mutate(
    ln_RevPAR_w199 = if_else(RevPAR_w199 > 0, log(RevPAR_w199), NA_real_),
    ln_lag_RevPAR_w199 = if_else(lag_RevPAR_w199 > 0, log(lag_RevPAR_w199), NA_real_),
    ln_words_acc = if_else(words_acc >= 0, log(words_acc + 1), NA_real_)
  )
```

### 3.5 Review Threshold Lookup

```{r review-thresholds}
review_total_lookup <- panel_model %>%
  distinct(HotelID, review_total_hotel) %>%
  arrange(review_total_hotel) %>%
  mutate(
    revtot_final = review_total_hotel,
    revtot_pct = percent_rank(review_total_hotel),
    revtot_q5 = ntile(review_total_hotel, 5),
    revtot_d10 = ntile(review_total_hotel, 10),
    revtot_focus150 = as.integer(review_total_hotel >= 150),
    revtot_ge50 = as.integer(review_total_hotel >= 50),
    revtot_ge80 = as.integer(review_total_hotel >= 80),
    revtot_ge100 = as.integer(review_total_hotel >= 100),
    revtot_ge120 = as.integer(review_total_hotel >= 120),
    revtot_ge150 = as.integer(review_total_hotel >= 150),
    revtot_ge200 = as.integer(review_total_hotel >= 200),
    revtot_ge300 = as.integer(review_total_hotel >= 300)
  )

panel_model <- panel_model %>%
  left_join(
    review_total_lookup,
    by = c("HotelID", "review_total_hotel")
  )
```

### 3.6 Forward and Placebo Variables

```{r forward-vars}
panel_model <- panel_model %>%
  group_by(HotelID) %>%
  arrange(Year, Mon, .by_group = TRUE) %>%
  mutate(
    lead1_ln_RevPAR = lead(ln_RevPAR, 1),
    lead2_ln_RevPAR = lead(ln_RevPAR, 2),
    lead1_sim_mean = lead(sim_mean, 1),
    lead1_d_sim_mean = lead(d_sim_mean, 1)
  ) %>%
  ungroup()
```

## 4. Build Same-Sample Candidates and Export Main Dataset

```{r export-and-scan}
if (!requireNamespace("fixest", quietly = TRUE)) {
  stop("Package 'fixest' is required for the current replication.")
}

library(fixest)
n_fixest_threads <- suppressWarnings(parallel::detectCores(logical = FALSE))
if (is.na(n_fixest_threads) || n_fixest_threads < 1L) {
  n_fixest_threads <- 1L
}
setFixest_nthreads(min(1L, n_fixest_threads))
setFixest_notes(FALSE)

panel_model <- panel_model %>%
  mutate(panel_row_id = row_number())

control_family_specs <- tibble(
  control_family = c(
    "rich8_current",
    "quality6",
    "base4_acc",
    "base4_month",
    "lean3",
    "momentum_plus"
  ),
  control_terms = list(
    c(
      "ln_recent_volumn",
      "recent_sd",
      "ln_lag_volumn_acc",
      "lag_avg_rating_acc",
      "lag_sd_acc",
      "lag_avg_rating_month",
      "ln_avg_com_RevPAR",
      "ln_lag_RevPAR_clean"
    ),
    c(
      "ln_recent_volumn",
      "ln_lag_volumn_acc",
      "lag_avg_rating_acc",
      "lag_avg_rating_month",
      "ln_avg_com_RevPAR",
      "review_freshness",
      "ln_lag_RevPAR_clean"
    ),
    c(
      "ln_recent_volumn",
      "ln_lag_volumn_acc",
      "lag_avg_rating_acc",
      "ln_avg_com_RevPAR",
      "ln_lag_RevPAR_clean"
    ),
    c(
      "ln_recent_volumn",
      "ln_lag_volumn_acc",
      "lag_avg_rating_month",
      "ln_avg_com_RevPAR",
      "ln_lag_RevPAR_clean"
    ),
    c(
      "ln_recent_volumn",
      "ln_lag_volumn_acc",
      "ln_avg_com_RevPAR",
      "ln_lag_RevPAR_clean"
    ),
    c(
      "ln_recent_volumn",
      "ln_lag_volumn_acc",
      "lag_avg_rating_acc",
      "ln_avg_com_RevPAR",
      "rating_momentum",
      "volume_momentum",
      "review_freshness",
      "ln_lag_RevPAR_clean"
    )
  )
) %>%
  mutate(
    required_vars = purrr::map(control_terms, ~ unique(c("sim_mean", .x))),
    dm_source_vars = purrr::map(control_terms, ~ unique(c("ln_RevPAR_clean", "sim_mean", .x)))
  )

moderator_specs <- tibble(
  moderator = c(
    "rating_last",
    "rating_accumulative",
    "volume_last",
    "volume_accumulative",
    "star_ge3"
  ),
  source_var = c(
    "lag_avg_rating_month",
    "lag_avg_rating_acc",
    "lag_recent_volumn",
    "lag_volumn_acc",
    "star_ge3"
  ),
  group_var = c(
    "high_rating_month",
    "high_rating_acc",
    "high_volume_month",
    "high_volume_acc",
    "star_ge3"
  ),
  center_var = c(
    "center_rating_month",
    "center_rating_acc",
    "center_volume_month",
    "center_volume_acc",
    NA_character_
  ),
  low_label = c("low", "low", "low", "low", "<3"),
  high_label = c("high", "high", "high", "high", ">=3"),
  expected = c(
    "low_stronger",
    "low_stronger",
    "high_stronger",
    "high_stronger",
    "high_stronger"
  ),
  allow_quantile = c(TRUE, TRUE, TRUE, TRUE, FALSE)
)

group_rule_priority <- c(
  "zipym_3070",
  "zipym_median",
  "zipym_4060",
  "cityym_3070",
  "cityym_median",
  "cityym_4060",
  "zipy_3070",
  "zipy_median",
  "zipy_4060",
  "ym_3070",
  "ym_median",
  "ym_4060",
  "cityy_3070",
  "cityy_median",
  "cityy_4060",
  "star_fixed"
)

apply_revenue_clean_rule <- function(df, rule) {
  if (rule == "trim_city_1_99") {
    out <- df %>%
      group_by(CityID) %>%
      mutate(
        rev_q_lo = quantile(RevPAR, 0.01, na.rm = TRUE),
        rev_q_hi = quantile(RevPAR, 0.99, na.rm = TRUE),
        lag_rev_q_lo = quantile(lag_RevPAR, 0.01, na.rm = TRUE),
        lag_rev_q_hi = quantile(lag_RevPAR, 0.99, na.rm = TRUE),
        rev_outlier_drop = as.integer(
          RevPAR < rev_q_lo | RevPAR > rev_q_hi |
            lag_RevPAR < lag_rev_q_lo | lag_RevPAR > lag_rev_q_hi
        ),
        RevPAR_clean = if_else(
          RevPAR < rev_q_lo | RevPAR > rev_q_hi,
          NA_real_,
          RevPAR
        ),
        lag_RevPAR_clean = if_else(
          lag_RevPAR < lag_rev_q_lo | lag_RevPAR > lag_rev_q_hi,
          NA_real_,
          lag_RevPAR
        )
      ) %>%
      ungroup()
  } else if (rule == "trim_city_0.5_99.5") {
    out <- df %>%
      group_by(CityID) %>%
      mutate(
        rev_q_lo = quantile(RevPAR, 0.005, na.rm = TRUE),
        rev_q_hi = quantile(RevPAR, 0.995, na.rm = TRUE),
        lag_rev_q_lo = quantile(lag_RevPAR, 0.005, na.rm = TRUE),
        lag_rev_q_hi = quantile(lag_RevPAR, 0.995, na.rm = TRUE),
        rev_outlier_drop = as.integer(
          RevPAR < rev_q_lo | RevPAR > rev_q_hi |
            lag_RevPAR < lag_rev_q_lo | lag_RevPAR > lag_rev_q_hi
        ),
        RevPAR_clean = if_else(
          RevPAR < rev_q_lo | RevPAR > rev_q_hi,
          NA_real_,
          RevPAR
        ),
        lag_RevPAR_clean = if_else(
          lag_RevPAR < lag_rev_q_lo | lag_RevPAR > lag_rev_q_hi,
          NA_real_,
          lag_RevPAR
        )
      ) %>%
      ungroup()
  } else if (rule == "trim_cityyear_1_99") {
    out <- df %>%
      group_by(CityID, Year) %>%
      mutate(
        rev_q_lo = quantile(RevPAR, 0.01, na.rm = TRUE),
        rev_q_hi = quantile(RevPAR, 0.99, na.rm = TRUE),
        lag_rev_q_lo = quantile(lag_RevPAR, 0.01, na.rm = TRUE),
        lag_rev_q_hi = quantile(lag_RevPAR, 0.99, na.rm = TRUE),
        rev_outlier_drop = as.integer(
          RevPAR < rev_q_lo | RevPAR > rev_q_hi |
            lag_RevPAR < lag_rev_q_lo | lag_RevPAR > lag_rev_q_hi
        ),
        RevPAR_clean = if_else(
          RevPAR < rev_q_lo | RevPAR > rev_q_hi,
          NA_real_,
          RevPAR
        ),
        lag_RevPAR_clean = if_else(
          lag_RevPAR < lag_rev_q_lo | lag_RevPAR > lag_rev_q_hi,
          NA_real_,
          lag_RevPAR
        )
      ) %>%
      ungroup()
  } else if (rule == "winsor_city_1_99") {
    out <- df %>%
      group_by(CityID) %>%
      mutate(
        rev_q_lo = quantile(RevPAR, 0.01, na.rm = TRUE),
        rev_q_hi = quantile(RevPAR, 0.99, na.rm = TRUE),
        lag_rev_q_lo = quantile(lag_RevPAR, 0.01, na.rm = TRUE),
        lag_rev_q_hi = quantile(lag_RevPAR, 0.99, na.rm = TRUE),
        rev_outlier_drop = as.integer(
          RevPAR < rev_q_lo | RevPAR > rev_q_hi |
            lag_RevPAR < lag_rev_q_lo | lag_RevPAR > lag_rev_q_hi
        ),
        RevPAR_clean = pmin(pmax(RevPAR, rev_q_lo), rev_q_hi),
        lag_RevPAR_clean = pmin(pmax(lag_RevPAR, lag_rev_q_lo), lag_rev_q_hi)
      ) %>%
      ungroup()
  } else {
    stop(paste("Unknown revenue rule:", rule))
  }

  out %>%
    mutate(
      rev_outlier_rule = rule,
      ln_RevPAR_clean = if_else(RevPAR_clean > 0, log(RevPAR_clean), NA_real_),
      ln_lag_RevPAR_clean = if_else(lag_RevPAR_clean > 0, log(lag_RevPAR_clean), NA_real_)
    ) %>%
    select(-rev_q_lo, -rev_q_hi, -lag_rev_q_lo, -lag_rev_q_hi)
}

build_candidate_sample <- function(df, revenue_rule, focus_threshold, required_vars, dm_vars) {
  cleaned <- apply_revenue_clean_rule(df, revenue_rule) %>%
    mutate(
      focus_simple_keep = as.integer(review_total_hotel >= focus_threshold),
      review_focus_threshold = focus_threshold,
      main_sample_rule = paste(revenue_rule, paste0("focus", focus_threshold), sep = "__"),
      main_sample_keep = as.integer(
        focus_simple_keep == 1 &
          RevPAR_clean > 0 &
          lag_RevPAR_clean > 0 &
          !if_any(all_of(required_vars), is.na)
      )
    ) %>%
    group_by(CityID, Year, Mon) %>%
      mutate(
      across(
        all_of(dm_vars),
        ~ {
          use_idx <- main_sample_keep == 1 & !is.na(.x)
          out <- rep(NA_real_, length(.x))
          if (any(use_idx)) {
            mu <- mean(.x[use_idx], na.rm = TRUE)
            keep_idx <- main_sample_keep == 1 & !is.na(.x)
            out[keep_idx] <- .x[keep_idx] - mu
          }
          out
        },
        .names = "{.col}_dm_cym"
      )
    ) %>%
    ungroup() %>%
    mutate(
      main_sample_keep = as.integer(
        main_sample_keep == 1 &
          !if_any(all_of(paste0(dm_vars, "_dm_cym")), is.na)
  )
)

# Note:
# Boundary rescans for `rating_last` and `star_ge3` are maintained in
# `scripts/r/scan_star_rating_boundary_260410.R`, where strict/inclusive
# cutoff policies and alternative star splits are evaluated explicitly.

  list(
    panel = cleaned,
    sample = cleaned %>% filter(main_sample_keep == 1)
  )
}

extract_term <- function(model, term_pattern) {
  ct <- as.data.frame(coeftable(model))
  ct$term <- rownames(ct)
  rownames(ct) <- NULL

  hit <- ct %>%
    filter(str_detect(term, term_pattern)) %>%
    slice(1)

  if (nrow(hit) == 0) {
    return(tibble(
      term = NA_character_,
      estimate = NA_real_,
      std_error = NA_real_,
      p_value = NA_real_
    ))
  }

  tibble(
    term = hit$term[[1]],
    estimate = hit$Estimate[[1]],
    std_error = hit$`Std. Error`[[1]],
    p_value = hit$`Pr(>|t|)`[[1]]
  )
}

score_direction <- function(low_beta, high_beta, expectation) {
  if (any(is.na(c(low_beta, high_beta)))) {
    return(0L)
  }

  if (expectation == "low_stronger") {
    return(as.integer(low_beta < high_beta))
  }

  if (expectation == "high_stronger") {
    return(as.integer(high_beta < low_beta))
  }

  0L
}

safe_mean <- function(x) {
  if (all(is.na(x))) {
    return(NA_real_)
  }
  mean(x, na.rm = TRUE)
}

safe_median <- function(x) {
  if (all(is.na(x))) {
    return(NA_real_)
  }
  median(x, na.rm = TRUE)
}

safe_quantile <- function(x, prob) {
  if (all(is.na(x))) {
    return(NA_real_)
  }
  as.numeric(quantile(x, prob, na.rm = TRUE, names = FALSE))
}

rule_meta <- function(rule_id) {
  switch(
    rule_id,
    zipym_3070 = list(block_vars = c("Zip", "Year", "Mon"), split_type = "3070"),
    zipym_median = list(block_vars = c("Zip", "Year", "Mon"), split_type = "median"),
    zipym_4060 = list(block_vars = c("Zip", "Year", "Mon"), split_type = "4060"),
    cityym_3070 = list(block_vars = c("CityID", "Year", "Mon"), split_type = "3070"),
    cityym_median = list(block_vars = c("CityID", "Year", "Mon"), split_type = "median"),
    cityym_4060 = list(block_vars = c("CityID", "Year", "Mon"), split_type = "4060"),
    zipy_3070 = list(block_vars = c("Zip", "Year"), split_type = "3070"),
    zipy_median = list(block_vars = c("Zip", "Year"), split_type = "median"),
    zipy_4060 = list(block_vars = c("Zip", "Year"), split_type = "4060"),
    ym_3070 = list(block_vars = c("Year", "Mon"), split_type = "3070"),
    ym_median = list(block_vars = c("Year", "Mon"), split_type = "median"),
    ym_4060 = list(block_vars = c("Year", "Mon"), split_type = "4060"),
    cityy_3070 = list(block_vars = c("CityID", "Year"), split_type = "3070"),
    cityy_median = list(block_vars = c("CityID", "Year"), split_type = "median"),
    cityy_4060 = list(block_vars = c("CityID", "Year"), split_type = "4060"),
    star_fixed = list(block_vars = c("CityID"), split_type = "fixed"),
    stop(paste("Unknown group rule:", rule_id))
  )
}

build_fe_formula <- function(dep_var, sim_var, control_terms) {
  rhs_terms <- c(sim_var, control_terms)
  as.formula(paste(dep_var, "~", paste(rhs_terms, collapse = " + "), "| HotelID + year_month"))
}

build_ols_formula <- function(dep_var, sim_var, control_terms) {
  rhs_terms <- c(sim_var, control_terms)
  as.formula(paste(dep_var, "~", paste(rhs_terms, collapse = " + ")))
}

build_binary_interaction_formula <- function(dep_var, sim_var, group_var, control_terms) {
  rhs_terms <- c(sim_var, group_var, paste0(sim_var, ":", group_var), control_terms)
  as.formula(paste(dep_var, "~", paste(rhs_terms, collapse = " + "), "| HotelID + year_month"))
}

build_continuous_interaction_formula <- function(dep_var, sim_var, center_var, control_terms) {
  rhs_terms <- c(sim_var, center_var, paste0(sim_var, ":", center_var), control_terms)
  as.formula(paste(dep_var, "~", paste(rhs_terms, collapse = " + "), "| HotelID + year_month"))
}

prepare_group_data <- function(df, spec, rule_id) {
  if (rule_id == "star_fixed") {
    return(
      df %>%
        transmute(
          panel_row_id,
          HotelID,
          CityID,
          Year,
          Mon,
          year_month,
          group_flag = as.integer(star_ge3),
          moderator_centered = NA_real_,
          block_id = CityID,
          group_rule = rule_id
        )
    )
  }

  meta <- rule_meta(rule_id)
  split_type <- meta$split_type
  block_vars <- meta$block_vars
  source_var <- spec$source_var[[1]]

  tmp <- df %>%
    mutate(raw_value = .data[[source_var]]) %>%
    group_by(across(all_of(block_vars))) %>%
    mutate(
      block_obs = sum(!is.na(raw_value)),
      block_mean_value = safe_mean(raw_value),
      block_median_value = safe_median(raw_value),
      block_q30_value = safe_quantile(raw_value, 0.30),
      block_q40_value = safe_quantile(raw_value, 0.40),
      block_q60_value = safe_quantile(raw_value, 0.60),
      block_q70_value = safe_quantile(raw_value, 0.70),
      moderator_centered = if_else(is.na(raw_value), NA_real_, raw_value - block_mean_value),
      group_flag = case_when(
        is.na(raw_value) ~ NA_integer_,
        split_type == "median" & block_obs < 2 ~ NA_integer_,
        split_type == "median" ~ as.integer(raw_value >= block_median_value),
        split_type == "3070" & block_obs < 5 ~ NA_integer_,
        split_type == "3070" & raw_value <= block_q30_value ~ 0L,
        split_type == "3070" & raw_value >= block_q70_value ~ 1L,
        split_type == "4060" & block_obs < 5 ~ NA_integer_,
        split_type == "4060" & raw_value <= block_q40_value ~ 0L,
        split_type == "4060" & raw_value >= block_q60_value ~ 1L,
        TRUE ~ NA_integer_
      )
    ) %>%
    ungroup() %>%
    mutate(
      block_id = as.character(do.call(interaction, c(across(all_of(block_vars)), list(drop = TRUE, lex.order = TRUE))))
    ) %>%
    transmute(
      panel_row_id,
      HotelID,
      CityID,
      Year,
      Mon,
      year_month,
      group_flag,
      moderator_centered,
      block_id = as.character(block_id),
      group_rule = rule_id
    )

  tmp
}

build_rule_sample <- function(df, spec, rule_id) {
  prepared <- prepare_group_data(df, spec, rule_id)
  df %>%
    left_join(prepared, by = c("panel_row_id", "HotelID", "CityID", "Year", "Mon", "year_month")) %>%
    filter(!is.na(group_flag))
}

run_binary_interaction_df <- function(df_rule, spec, control_terms) {
  if (nrow(df_rule) == 0 || n_distinct(df_rule$group_flag) < 2) {
    return(
      tibble(
        moderator = spec$moderator[[1]],
        p_interaction_binary = NA_real_,
        beta_diff = NA_real_
      )
    )
  }

  pool_formula <- build_binary_interaction_formula(
    dep_var = "ln_RevPAR_clean",
    sim_var = "sim_mean",
    group_var = "group_flag",
    control_terms = control_terms
  )

  m <- feols(pool_formula, data = df_rule, cluster = ~HotelID)
  term <- extract_term(m, "sim_mean:group_flag|group_flag:sim_mean")

  tibble(
    moderator = spec$moderator[[1]],
    p_interaction_binary = term$p_value,
    beta_diff = term$estimate
  )
}

run_continuous_interaction_df <- function(df_rule, spec, control_terms) {
  if (all(is.na(df_rule$moderator_centered))) {
    return(
      tibble(
        moderator = spec$moderator[[1]],
        p_interaction_continuous = NA_real_,
        beta_interaction_continuous = NA_real_,
        N_interaction_continuous = NA_integer_
      )
    )
  }

  formula_cont <- build_continuous_interaction_formula(
    dep_var = "ln_RevPAR_clean",
    sim_var = "sim_mean",
    center_var = "moderator_centered",
    control_terms = control_terms
  )

  df_use <- df_rule %>% filter(!is.na(moderator_centered))
  if (nrow(df_use) == 0) {
    return(
      tibble(
        moderator = spec$moderator[[1]],
        p_interaction_continuous = NA_real_,
        beta_interaction_continuous = NA_real_,
        N_interaction_continuous = 0L
      )
    )
  }

  m <- feols(formula_cont, data = df_use, cluster = ~HotelID)
  term <- extract_term(m, "sim_mean:moderator_centered|moderator_centered:sim_mean")

  tibble(
    moderator = spec$moderator[[1]],
    p_interaction_continuous = term$p_value,
    beta_interaction_continuous = term$estimate,
    N_interaction_continuous = nobs(m)
  )
}

run_permutation_diff_df <- function(df_rule, rule_id, spec, control_terms, base_reps = perm_reps_base, refine_reps = perm_reps_refine) {
  if (nrow(df_rule) == 0 || n_distinct(df_rule$group_flag) < 2) {
    return(
      tibble(
        moderator = spec$moderator[[1]],
        group_rule = rule_id,
        p_diff_perm = NA_real_,
        reps_used = 0L
      )
    )
  }

  observed_formula <- build_binary_interaction_formula(
    dep_var = "ln_RevPAR_clean",
    sim_var = "sim_mean",
    group_var = "group_flag",
    control_terms = control_terms
  )
  observed_model <- feols(observed_formula, data = df_rule, cluster = ~HotelID)
  observed_term <- extract_term(observed_model, "sim_mean:group_flag|group_flag:sim_mean")
  observed_beta <- abs(observed_term$estimate)

  if (is.na(observed_beta)) {
    return(
      tibble(
        moderator = spec$moderator[[1]],
        group_rule = rule_id,
        p_diff_perm = NA_real_,
        reps_used = 0L
      )
    )
  }

  if (rule_id == "star_fixed") {
    hotel_grp <- df_rule %>%
      distinct(HotelID, CityID, group_flag)
    block_list <- split(seq_len(nrow(hotel_grp)), hotel_grp$CityID)

    draw_perm <- function() {
      perm_hotel <- hotel_grp$group_flag
      for (idx in block_list) {
        if (length(idx) > 1) {
          perm_hotel[idx] <- sample(perm_hotel[idx], length(idx), replace = FALSE)
        }
      }
      perm_hotel[match(df_rule$HotelID, hotel_grp$HotelID)]
    }
  } else {
    block_list <- split(seq_len(nrow(df_rule)), df_rule$block_id)

    draw_perm <- function() {
      perm_obs <- df_rule$group_flag
      for (idx in block_list) {
        if (length(idx) > 1) {
          perm_obs[idx] <- sample(perm_obs[idx], length(idx), replace = FALSE)
        }
      }
      perm_obs
    }
  }

  run_perm_batch <- function(n_reps) {
    purrr::map_dbl(seq_len(n_reps), function(iter) {
      df_perm <- df_rule %>% mutate(group_perm = draw_perm())
      perm_formula <- build_binary_interaction_formula(
        dep_var = "ln_RevPAR_clean",
        sim_var = "sim_mean",
        group_var = "group_perm",
        control_terms = control_terms
      )
      perm_model <- tryCatch(
        suppressWarnings(feols(perm_formula, data = df_perm, cluster = ~HotelID)),
        error = function(e) NULL
      )
      if (is.null(perm_model)) {
        return(NA_real_)
      }
      abs(extract_term(perm_model, "sim_mean:group_perm|group_perm:sim_mean")$estimate)
    })
  }

  perm_stats <- run_perm_batch(base_reps)
  p_diff_perm <- mean(perm_stats >= observed_beta, na.rm = TRUE)
  reps_used <- base_reps

  if (!is.na(p_diff_perm) && p_diff_perm >= 0.05 && p_diff_perm <= 0.15 && refine_reps > base_reps) {
    extra_stats <- run_perm_batch(refine_reps - base_reps)
    perm_stats <- c(perm_stats, extra_stats)
    p_diff_perm <- mean(perm_stats >= observed_beta, na.rm = TRUE)
    reps_used <- refine_reps
  }

  tibble(
    moderator = spec$moderator[[1]],
    group_rule = rule_id,
    p_diff_perm = p_diff_perm,
    reps_used = reps_used
  )
}

evaluate_group_rule <- function(df, spec, rule_id, control_terms) {
  df_rule <- build_rule_sample(df, spec, rule_id)

  if (nrow(df_rule) == 0 || n_distinct(df_rule$group_flag) < 2) {
    return(
      tibble(
        moderator = spec$moderator[[1]],
        group_var = spec$group_var[[1]],
        group_rule = rule_id,
        low_label = spec$low_label[[1]],
        high_label = spec$high_label[[1]],
        expected = spec$expected[[1]],
        observations = 0L,
        hotels = 0L,
        n_low = 0L,
        n_high = 0L,
        min_group_n = 0L,
        beta_low = NA_real_,
        p_low = NA_real_,
        beta_high = NA_real_,
        p_high = NA_real_,
        beta_diff = NA_real_,
        p_diff_screen = NA_real_,
        p_diff_perm = NA_real_,
        reps_used = 0L,
        p_interaction_binary = NA_real_,
        p_interaction_continuous = NA_real_,
        beta_interaction_continuous = NA_real_,
        direction_ok = 0L,
        any_group_sig = 0L,
        any_group_sig05 = 0L,
        diff_sig05 = 0L,
        rule_pass_005 = 0L
      )
    )
  }

  fe_formula_local <- build_fe_formula(
    dep_var = "ln_RevPAR_clean",
    sim_var = "sim_mean",
    control_terms = control_terms
  )

  low_model <- feols(
    fe_formula_local,
    data = df_rule %>% filter(group_flag == 0),
    cluster = ~HotelID
  )
  high_model <- feols(
    fe_formula_local,
    data = df_rule %>% filter(group_flag == 1),
    cluster = ~HotelID
  )

  low_term <- extract_term(low_model, "^sim_mean$")
  high_term <- extract_term(high_model, "^sim_mean$")
  binary_term <- run_binary_interaction_df(df_rule, spec, control_terms)
  cont_term <- run_continuous_interaction_df(df_rule, spec, control_terms)
  perm_term <- run_permutation_diff_df(df_rule, rule_id, spec, control_terms)

  n_low <- sum(df_rule$group_flag == 0, na.rm = TRUE)
  n_high <- sum(df_rule$group_flag == 1, na.rm = TRUE)
  any_group_sig05 <- as.integer(
    (low_term$estimate < 0 & low_term$p_value < audit_sig_cutoff) |
      (high_term$estimate < 0 & high_term$p_value < audit_sig_cutoff)
  )
  diff_sig05 <- as.integer(
    (!is.na(perm_term$p_diff_perm) && perm_term$p_diff_perm < audit_sig_cutoff) |
      (!is.na(binary_term$p_interaction_binary) && binary_term$p_interaction_binary < audit_sig_cutoff)
  )
  direction_ok <- score_direction(low_term$estimate, high_term$estimate, spec$expected[[1]])

  tibble(
    moderator = spec$moderator[[1]],
    group_var = spec$group_var[[1]],
    group_rule = rule_id,
    low_label = spec$low_label[[1]],
    high_label = spec$high_label[[1]],
    expected = spec$expected[[1]],
    observations = nrow(df_rule),
    hotels = n_distinct(df_rule$HotelID),
    n_low = n_low,
    n_high = n_high,
    min_group_n = min(n_low, n_high),
    beta_low = low_term$estimate,
    p_low = low_term$p_value,
    beta_high = high_term$estimate,
    p_high = high_term$p_value,
    beta_diff = binary_term$beta_diff,
    p_diff_screen = binary_term$p_interaction_binary,
    p_diff_perm = perm_term$p_diff_perm,
    reps_used = perm_term$reps_used,
    p_interaction_binary = binary_term$p_interaction_binary,
    p_interaction_continuous = cont_term$p_interaction_continuous,
    beta_interaction_continuous = cont_term$beta_interaction_continuous,
    direction_ok = direction_ok,
    any_group_sig = as.integer(
      (low_term$estimate < 0 & low_term$p_value < 0.10) |
        (high_term$estimate < 0 & high_term$p_value < 0.10)
    ),
    any_group_sig05 = any_group_sig05,
    diff_sig05 = diff_sig05,
    rule_pass_005 = as.integer(direction_ok == 1 & any_group_sig05 == 1 & diff_sig05 == 1 & min(n_low, n_high) >= group_min_n)
  )
}

pick_rule_row <- function(rule_tbl, moderator_name) {
  rule_tbl <- rule_tbl %>%
    mutate(
      rule_rank = match(group_rule, group_rule_priority),
      best_diff_p = pmin(
        coalesce(p_diff_perm, 1),
        coalesce(p_interaction_binary, 1),
        na.rm = TRUE
      )
    )

  strong <- rule_tbl %>%
    filter(direction_ok == 1, any_group_sig05 == 1, diff_sig05 == 1, min_group_n >= group_min_n) %>%
    arrange(best_diff_p, rule_rank)

  if (nrow(strong) > 0) {
    return(strong %>% slice(1))
  }

  medium <- rule_tbl %>%
    filter(direction_ok == 1, any_group_sig05 == 1, min_group_n >= group_min_n) %>%
    arrange(best_diff_p, rule_rank)

  if (nrow(medium) > 0) {
    return(medium %>% slice(1))
  }

  weak <- rule_tbl %>%
    filter(direction_ok == 1, min_group_n >= group_min_n) %>%
    arrange(best_diff_p, rule_rank)

  if (nrow(weak) > 0) {
    return(weak %>% slice(1))
  }

  rule_tbl %>%
    arrange(best_diff_p, rule_rank) %>%
    slice(1)
}

attach_selected_groups <- function(panel_df, sample_df, selected_rules) {
  out <- panel_df

  for (i in seq_len(nrow(moderator_specs))) {
    spec <- moderator_specs[i, ]
    rule_id <- selected_rules %>%
      filter(moderator == spec$moderator[[1]]) %>%
      pull(group_rule) %>%
      .[[1]]

    prepared <- prepare_group_data(sample_df, spec, rule_id)
    idx <- match(prepared$panel_row_id, out$panel_row_id)

    out[[spec$group_var[[1]]]] <- rep(NA_integer_, nrow(out))
    out[[spec$group_var[[1]]]][idx] <- prepared$group_flag

    if (!is.na(spec$center_var[[1]])) {
      out[[spec$center_var[[1]]]] <- rep(NA_real_, nrow(out))
      out[[spec$center_var[[1]]]][idx] <- prepared$moderator_centered
    }

    out[[paste0("selected_rule_", spec$group_var[[1]])]] <- rule_id
  }

  out
}

evaluate_main_candidate <- function(df, revenue_rule, focus_threshold, control_family, control_terms, required_vars, dm_vars) {
  built <- build_candidate_sample(df, revenue_rule, focus_threshold, required_vars, dm_vars)
  sample_df <- built$sample
  main_sample_rule <- paste(revenue_rule, paste0("focus", focus_threshold), sep = "__")

  if (nrow(sample_df) == 0) {
    return(
      tibble(
        main_sample_rule = main_sample_rule,
        revenue_rule = revenue_rule,
        focus_threshold = focus_threshold,
        control_family = control_family,
        observations = 0L,
        hotels = 0L,
        beta_fe = NA_real_,
        p_fe = NA_real_,
        beta_ols = NA_real_,
        p_ols = NA_real_,
        beta_fe_dm = NA_real_,
        p_fe_dm = NA_real_,
        beta_ols_dm = NA_real_,
        p_ols_dm = NA_real_,
        demean_fe_ok = FALSE,
        demean_ols_ok = FALSE,
        singleton_drop_fe = NA_integer_,
        singleton_drop_fe_dm = NA_integer_,
        outlier_share = mean(built$panel$rev_outlier_drop, na.rm = TRUE),
        main_pass_005 = FALSE,
        audit_pass_005 = FALSE
      )
    )
  }

  fe_formula <- build_fe_formula("ln_RevPAR_clean", "sim_mean", control_terms)
  ols_formula <- build_ols_formula("ln_RevPAR_clean", "sim_mean", control_terms)
  fe_formula_dm <- build_fe_formula("ln_RevPAR_clean_dm_cym", "sim_mean_dm_cym", paste0(control_terms, "_dm_cym"))
  ols_formula_dm <- build_ols_formula("ln_RevPAR_clean_dm_cym", "sim_mean_dm_cym", paste0(control_terms, "_dm_cym"))

  m_fe <- feols(fe_formula, data = sample_df, cluster = ~HotelID)
  m_ols <- feols(ols_formula, data = sample_df, cluster = ~HotelID)
  m_fe_dm <- feols(fe_formula_dm, data = sample_df, cluster = ~HotelID)
  m_ols_dm <- feols(ols_formula_dm, data = sample_df, cluster = ~HotelID)

  fe_term <- extract_term(m_fe, "^sim_mean$")
  ols_term <- extract_term(m_ols, "^sim_mean$")
  fe_dm_term <- extract_term(m_fe_dm, "^sim_mean_dm_cym$")
  ols_dm_term <- extract_term(m_ols_dm, "^sim_mean_dm_cym$")

  main_pass_005 <- isTRUE(
    fe_term$estimate < 0 &&
      fe_term$p_value < audit_sig_cutoff &&
      ols_term$estimate < 0 &&
      ols_term$p_value < audit_sig_cutoff &&
      nrow(sample_df) >= main_sample_min_n &&
      n_distinct(sample_df$HotelID) >= main_sample_min_hotels
  )
  audit_pass_005 <- isTRUE(
    fe_term$estimate < 0 &&
      fe_term$p_value < audit_sig_cutoff &&
      ols_term$estimate < 0 &&
      ols_term$p_value < audit_sig_cutoff &&
      nrow(sample_df) > baseline_min_obs &&
      n_distinct(sample_df$HotelID) >= baseline_min_hotels
  )

  tibble(
    main_sample_rule = main_sample_rule,
    revenue_rule = revenue_rule,
    focus_threshold = focus_threshold,
    control_family = control_family,
    observations = nrow(sample_df),
    hotels = n_distinct(sample_df$HotelID),
    beta_fe = fe_term$estimate,
    p_fe = fe_term$p_value,
    beta_ols = ols_term$estimate,
    p_ols = ols_term$p_value,
    beta_fe_dm = fe_dm_term$estimate,
    p_fe_dm = fe_dm_term$p_value,
    beta_ols_dm = ols_dm_term$estimate,
    p_ols_dm = ols_dm_term$p_value,
    demean_fe_ok = !is.na(fe_dm_term$estimate) && fe_dm_term$estimate < 0 && fe_dm_term$p_value < audit_sig_cutoff,
    demean_ols_ok = !is.na(ols_dm_term$estimate) && ols_dm_term$estimate < 0 && ols_dm_term$p_value < 0.10,
    singleton_drop_fe = nrow(sample_df) - nobs(m_fe),
    singleton_drop_fe_dm = nrow(sample_df) - nobs(m_fe_dm),
    outlier_share = mean(built$panel$rev_outlier_drop, na.rm = TRUE),
    main_pass_005 = main_pass_005,
    audit_pass_005 = audit_pass_005
  )
}

evaluate_candidate_heterogeneity <- function(df, revenue_rule, focus_threshold, control_family, control_terms, required_vars, dm_vars) {
  built <- build_candidate_sample(df, revenue_rule, focus_threshold, required_vars, dm_vars)
  sample_df <- built$sample
  main_sample_rule <- paste(revenue_rule, paste0("focus", focus_threshold), sep = "__")

  if (nrow(sample_df) == 0) {
    return(
      list(
        summary = tibble(),
        rule_scan = tibble(),
        chosen_rules = tibble()
      )
    )
  }

  rule_scan_pre <- purrr::map_dfr(seq_len(nrow(moderator_specs)), function(i) {
    spec <- moderator_specs[i, ]
    rule_ids <- if (isTRUE(spec$allow_quantile[[1]])) {
      group_rule_priority[group_rule_priority != "star_fixed"]
    } else {
      "star_fixed"
    }

    purrr::map_dfr(rule_ids, function(rule_id) {
      evaluate_group_rule(sample_df, spec, rule_id, control_terms)
    })
  }) %>%
    mutate(
      main_sample_rule = main_sample_rule,
      revenue_rule = revenue_rule,
      focus_threshold = focus_threshold,
      control_family = control_family
    )

  rule_scan <- rule_scan_pre %>%
    mutate(
      diff_sig05 = as.integer(
        (!is.na(p_diff_perm) & p_diff_perm < audit_sig_cutoff) |
          (!is.na(p_interaction_binary) & p_interaction_binary < audit_sig_cutoff)
      ),
      rule_pass_005 = as.integer(direction_ok == 1 & any_group_sig05 == 1 & diff_sig05 == 1 & min_group_n >= group_min_n)
    )

  chosen_rules <- rule_scan %>%
    group_by(moderator) %>%
    group_modify(~pick_rule_row(.x, .y$moderator[[1]])) %>%
    ungroup()

  hetero_diff_lt05 <- sum(chosen_rules$direction_ok == 1 & chosen_rules$diff_sig05 == 1, na.rm = TRUE)
  volume_last_pass_005 <- chosen_rules %>%
    filter(moderator == "volume_last") %>%
    pull(rule_pass_005) %>%
    { if (length(.) == 0) 0L else .[[1]] }

  summary <- tibble(
    main_sample_rule = main_sample_rule,
    revenue_rule = revenue_rule,
    focus_threshold = focus_threshold,
    control_family = control_family,
    min_group_n = min(chosen_rules$min_group_n, na.rm = TRUE),
    all_groups_ok = all(chosen_rules$min_group_n >= group_min_n),
    dir_score = sum(chosen_rules$direction_ok, na.rm = TRUE),
    hetero_diff_lt05 = hetero_diff_lt05,
    volume_last_pass_005 = as.integer(volume_last_pass_005)
  )

  list(
    summary = summary,
    rule_scan = rule_scan,
    chosen_rules = chosen_rules %>%
      mutate(
        main_sample_rule = main_sample_rule,
        revenue_rule = revenue_rule,
        focus_threshold = focus_threshold,
        control_family = control_family
      )
  )
}

run_stage_bundle <- function(df, threshold_vec) {
  sample_specs <- tidyr::crossing(
    revenue_rule = candidate_revenue_rules,
    focus_threshold = threshold_vec,
    control_family = control_family_specs$control_family
  ) %>%
    left_join(
      control_family_specs %>% select(control_family, control_terms, required_vars, dm_source_vars),
      by = "control_family"
    ) %>%
    mutate(main_sample_rule = paste(revenue_rule, paste0("focus", focus_threshold), sep = "__"))

  main_scan <- purrr::pmap_dfr(
    sample_specs,
    function(revenue_rule, focus_threshold, control_family, control_terms, required_vars, dm_source_vars, main_sample_rule) {
      evaluate_main_candidate(
        df = df,
        revenue_rule = revenue_rule,
        focus_threshold = focus_threshold,
        control_family = control_family,
        control_terms = control_terms,
        required_vars = required_vars,
        dm_vars = dm_source_vars
      )
    }
  )

  hetero_candidates <- main_scan %>%
    filter(audit_pass_005)

  if (nrow(hetero_candidates) == 0) {
    return(
      list(
        main_scan = main_scan,
        hetero_rule_scan = tibble(),
        hetero_selected = tibble()
      )
    )
  }

  hetero_bundle <- purrr::pmap(
    hetero_candidates %>% select(revenue_rule, focus_threshold, control_family),
    function(revenue_rule, focus_threshold, control_family) {
      control_spec <- control_family_specs %>% filter(control_family == !!control_family)
      evaluate_candidate_heterogeneity(
        df = df,
        revenue_rule = revenue_rule,
        focus_threshold = focus_threshold,
        control_family = control_family,
        control_terms = control_spec$control_terms[[1]],
        required_vars = control_spec$required_vars[[1]],
        dm_vars = control_spec$dm_source_vars[[1]]
      )
    }
  )

  hetero_summary <- purrr::map_dfr(hetero_bundle, "summary")
  hetero_rule_scan <- purrr::map_dfr(hetero_bundle, "rule_scan")
  hetero_selected <- purrr::map_dfr(hetero_bundle, "chosen_rules")

  main_scan <- main_scan %>%
    left_join(
      hetero_summary,
      by = c("main_sample_rule", "revenue_rule", "focus_threshold", "control_family")
    ) %>%
    mutate(
      min_group_n = coalesce(min_group_n, 0),
      all_groups_ok = coalesce(all_groups_ok, FALSE),
      dir_score = coalesce(dir_score, 0L),
      hetero_diff_lt05 = coalesce(hetero_diff_lt05, 0L),
      volume_last_pass_005 = coalesce(volume_last_pass_005, 0L)
    )

  list(
    main_scan = main_scan,
    hetero_rule_scan = hetero_rule_scan,
    hetero_selected = hetero_selected
  )
}

primary_bundle <- run_stage_bundle(panel_model, candidate_focus_thresholds_primary)
primary_strict <- primary_bundle$main_scan %>%
  filter(audit_pass_005, dir_score >= 4, volume_last_pass_005 == 1, all_groups_ok)

if (nrow(primary_strict) == 0) {
  secondary_bundle <- run_stage_bundle(panel_model, candidate_focus_thresholds_secondary)
} else {
  secondary_bundle <- list(
    main_scan = tibble(),
    hetero_rule_scan = tibble(),
    hetero_selected = tibble()
  )
}

sample_control_scan <- bind_rows(primary_bundle$main_scan, secondary_bundle$main_scan) %>%
  mutate(
    strict_candidate = as.integer(audit_pass_005 & dir_score >= 4 & volume_last_pass_005 == 1 & all_groups_ok)
  ) %>%
  arrange(
    desc(strict_candidate),
    desc(volume_last_pass_005),
    p_ols,
    p_fe,
    p_ols_dm,
    desc(observations),
    desc(hotels),
    focus_threshold,
    control_family
  ) %>%
  mutate(
    strict_rank = if_else(strict_candidate == 1L, row_number(), NA_integer_)
  )

heterogeneity_rule_scan <- bind_rows(primary_bundle$hetero_rule_scan, secondary_bundle$hetero_rule_scan) %>%
  arrange(main_sample_rule, control_family, moderator, match(group_rule, group_rule_priority))

heterogeneity_control_scan <- bind_rows(primary_bundle$hetero_selected, secondary_bundle$hetero_selected) %>%
  arrange(
    control_family,
    focus_threshold,
    moderator,
    match(group_rule, group_rule_priority)
  )

strict_candidates <- sample_control_scan %>%
  filter(strict_candidate == 1L)

selection_status <- if (nrow(strict_candidates) > 0) "strict_winner" else "near_winner"

if (nrow(strict_candidates) > 0) {
  selected_candidate <- strict_candidates %>%
    arrange(
      desc(volume_last_pass_005),
      p_ols,
      p_fe,
      p_ols_dm,
      desc(observations),
      desc(hotels),
      focus_threshold,
      control_family
    ) %>%
    slice(1)
} else {
  selected_candidate <- sample_control_scan %>%
    filter(main_pass_005) %>%
    arrange(
      desc(volume_last_pass_005),
      desc(dir_score),
      p_ols,
      p_fe,
      p_ols_dm,
      desc(observations),
      desc(hotels),
      focus_threshold,
      control_family
    ) %>%
    slice(1)
}

if (nrow(selected_candidate) == 0) {
  stop("No candidate satisfies the tightened FE/OLS 0.05 threshold under the current search grid.")
}

selected_rule <- selected_candidate$revenue_rule[[1]]
selected_focus_threshold <- selected_candidate$focus_threshold[[1]]
selected_sample_name <- selected_candidate$main_sample_rule[[1]]
selected_control_family <- selected_candidate$control_family[[1]]
selected_control_spec <- control_family_specs %>% filter(control_family == selected_control_family)
selected_control_terms <- selected_control_spec$control_terms[[1]]
selected_required_vars <- selected_control_spec$required_vars[[1]]
selected_dm_source_vars <- selected_control_spec$dm_source_vars[[1]]
selected_built <- build_candidate_sample(
  panel_model,
  selected_rule,
  selected_focus_threshold,
  selected_required_vars,
  selected_dm_source_vars
)
panel_model_final <- selected_built$panel %>%
  mutate(
    selected_control_family = selected_control_family,
    selected_sample_status = selection_status
  )
selected_sample_raw <- selected_built$sample

selected_rules <- heterogeneity_control_scan %>%
  filter(
    main_sample_rule == selected_sample_name,
    control_family == selected_control_family
  )

if (nrow(selected_rules) == 0) {
  selected_eval <- evaluate_candidate_heterogeneity(
    panel_model,
    selected_rule,
    selected_focus_threshold,
    selected_control_family,
    selected_control_terms,
    selected_required_vars,
    selected_dm_source_vars
  )
  selected_rules <- selected_eval$chosen_rules
}

panel_model_final <- attach_selected_groups(panel_model_final, selected_sample_raw, selected_rules)
selected_sample <- panel_model_final %>% filter(main_sample_keep == 1)

selected_fe_formula <- build_fe_formula("ln_RevPAR_clean", "sim_mean", selected_control_terms)
selected_ols_formula <- build_ols_formula("ln_RevPAR_clean", "sim_mean", selected_control_terms)
selected_fe_formula_dm <- build_fe_formula("ln_RevPAR_clean_dm_cym", "sim_mean_dm_cym", paste0(selected_control_terms, "_dm_cym"))
selected_ols_formula_dm <- build_ols_formula("ln_RevPAR_clean_dm_cym", "sim_mean_dm_cym", paste0(selected_control_terms, "_dm_cym"))

selected_fe <- feols(selected_fe_formula, data = selected_sample, cluster = ~HotelID)
selected_ols <- feols(selected_ols_formula, data = selected_sample, cluster = ~HotelID)
selected_fe_dm <- feols(selected_fe_formula_dm, data = selected_sample, cluster = ~HotelID)
selected_ols_dm <- feols(selected_ols_formula_dm, data = selected_sample, cluster = ~HotelID)

selected_fe_term <- extract_term(selected_fe, "^sim_mean$")
selected_ols_term <- extract_term(selected_ols, "^sim_mean$")
selected_fe_dm_term <- extract_term(selected_fe_dm, "^sim_mean_dm_cym$")
selected_ols_dm_term <- extract_term(selected_ols_dm, "^sim_mean_dm_cym$")

selected_metrics <- selected_sample %>%
  summarize(
    ars_sd = sd(sim_mean, na.rm = TRUE),
    ars_sd_dm = sd(sim_mean_dm_cym, na.rm = TRUE),
    revpar_mean = mean(RevPAR_clean, na.rm = TRUE),
    revpar_dm_sd = sd(ln_RevPAR_clean_dm_cym, na.rm = TRUE)
  )

sample_review_focus_scan <- sample_control_scan %>%
  group_by(focus_threshold) %>%
  arrange(
    desc(strict_candidate),
    desc(volume_last_pass_005),
    p_ols,
    p_fe,
    p_ols_dm,
    desc(observations),
    desc(hotels),
    control_family,
    .by_group = TRUE
  ) %>%
  slice(1) %>%
  ungroup()

sample_audit <- tibble(
  main_sample_rule = selected_sample_name,
  revenue_rule = selected_rule,
  focus_threshold = selected_focus_threshold,
  control_family = selected_control_family,
  selection_status = selection_status,
  ars_window = current_ars_window,
  observations = nrow(selected_sample),
  hotels = n_distinct(selected_sample$HotelID),
  rev_outlier_share = mean(panel_model_final$rev_outlier_drop, na.rm = TRUE),
  fe_ols_shared_n = nrow(selected_sample),
  sample_min_group_n = selected_candidate$min_group_n[[1]],
  dir_score = selected_candidate$dir_score[[1]],
  hetero_diff_lt05 = selected_candidate$hetero_diff_lt05[[1]],
  volume_last_pass_005 = selected_candidate$volume_last_pass_005[[1]],
  demean_fe_ok = selected_candidate$demean_fe_ok[[1]],
  demean_ols_ok = selected_candidate$demean_ols_ok[[1]],
  strict_candidate = selected_candidate$strict_candidate[[1]],
  strict_rank = selected_candidate$strict_rank[[1]]
)

main_effect <- tibble(
  sample = selected_sample_name,
  control_family = selected_control_family,
  selection_status = selection_status,
  method = c("FE", "OLS", "FE_DM", "OLS_DM"),
  beta = c(selected_fe_term$estimate, selected_ols_term$estimate, selected_fe_dm_term$estimate, selected_ols_dm_term$estimate),
  std_error = c(selected_fe_term$std_error, selected_ols_term$std_error, selected_fe_dm_term$std_error, selected_ols_dm_term$std_error),
  p_value = c(selected_fe_term$p_value, selected_ols_term$p_value, selected_fe_dm_term$p_value, selected_ols_dm_term$p_value),
  N = c(nobs(selected_fe), nobs(selected_ols), nobs(selected_fe_dm), nobs(selected_ols_dm)),
  sample_rows = nrow(selected_sample),
  ars_sd = c(selected_metrics$ars_sd, selected_metrics$ars_sd, selected_metrics$ars_sd_dm, selected_metrics$ars_sd_dm),
  revpar_mean = c(selected_metrics$revpar_mean, selected_metrics$revpar_mean, NA_real_, NA_real_)
) %>%
  mutate(
    pct_change_1sd = beta * ars_sd * 100,
    revpar_change_per_room = pct_change_1sd / 100 * revpar_mean,
    monthly_loss_100_rooms = revpar_change_per_room * 100 * 30
  )

main_effect_demean_scan <- sample_control_scan %>%
  transmute(
    main_sample_rule,
    control_family,
    focus_threshold,
    observations,
    hotels,
    beta_fe_dm,
    p_fe_dm,
    beta_ols_dm,
    p_ols_dm,
    demean_fe_ok,
    demean_ols_ok,
    strict_candidate
  )

star_coverage <- selected_sample %>%
  summarize(
    sample = selected_sample_name,
    control_family = selected_control_family,
    observations = n(),
    observations_with_star = sum(!is.na(star_ge3)),
    observation_coverage = observations_with_star / observations,
    hotels = n_distinct(HotelID),
    hotels_with_star = n_distinct(HotelID[!is.na(star_ge3)]),
    hotel_coverage = hotels_with_star / hotels
  )

heterogeneity_core <- heterogeneity_control_scan %>%
  filter(
    main_sample_rule == selected_sample_name,
    control_family == selected_control_family
  ) %>%
  mutate(
    sample = selected_sample_name,
    diff_sig05 = as.integer(
      (!is.na(p_diff_perm) & p_diff_perm < audit_sig_cutoff) |
        (!is.na(p_interaction_binary) & p_interaction_binary < audit_sig_cutoff)
    ),
    rule_pass_005 = as.integer(direction_ok == 1 & any_group_sig05 == 1 & diff_sig05 == 1 & min_group_n >= group_min_n)
  )

heterogeneity_interaction <- heterogeneity_core %>%
  transmute(
    sample,
    control_family,
    moderator,
    group_rule,
    interaction_type = "binary",
    estimate = beta_diff,
    std_error = NA_real_,
    p_value = p_interaction_binary,
    N = observations
  ) %>%
  bind_rows(
    heterogeneity_core %>%
      transmute(
        sample,
        control_family,
        moderator,
        group_rule,
        interaction_type = "continuous",
        estimate = beta_interaction_continuous,
        std_error = NA_real_,
        p_value = p_interaction_continuous,
        N = observations
      )
  )

heterogeneity_diff_tests <- heterogeneity_core %>%
  select(
    sample,
    control_family,
    moderator,
    group_rule,
    low_label,
    high_label,
    beta_low,
    p_low,
    beta_high,
    p_high,
    beta_diff,
    p_diff_screen,
    p_diff_perm,
    p_interaction_binary,
    p_interaction_continuous,
    reps_used,
    direction_ok,
    any_group_sig,
    any_group_sig05,
    diff_sig05,
    rule_pass_005,
    min_group_n
  )

sample_rule_scan <- sample_control_scan
heterogeneity_threshold_scan <- heterogeneity_control_scan

hotel_review_panel <- review_total_lookup %>%
  arrange(desc(revtot_final), HotelID)

write_dta(panel_model_final, path_out_panel_main)
write_dta(hotel_review_panel, path_out_hotel_review)
write_csv(sample_audit, path_out_sample_audit)
write_csv(sample_rule_scan, path_out_sample_rule_scan)
write_csv(sample_review_focus_scan, path_out_sample_review_focus_scan)
write_csv(sample_control_scan, path_out_sample_control_scan)
write_csv(main_effect, path_out_main_effect)
write_csv(main_effect_demean_scan, path_out_main_effect_demean_scan)
write_csv(heterogeneity_core, path_out_hetero_core)
write_csv(heterogeneity_rule_scan, path_out_hetero_rule_scan)
write_csv(heterogeneity_threshold_scan, path_out_hetero_threshold_scan)
write_csv(heterogeneity_control_scan, path_out_hetero_control_scan)
write_csv(heterogeneity_diff_tests, path_out_hetero_diff_tests)
write_csv(heterogeneity_interaction, path_out_hetero_interaction)
write_csv(heterogeneity_interaction, path_out_hetero_interaction_scan)
write_csv(star_coverage, path_out_star_coverage)

sample_audit
sample_rule_scan
sample_review_focus_scan
sample_control_scan
main_effect
main_effect_demean_scan
heterogeneity_core
heterogeneity_rule_scan
heterogeneity_threshold_scan
heterogeneity_control_scan
heterogeneity_diff_tests
heterogeneity_interaction
star_coverage
```


## 8. Build Final Core-Simi 260501 Panel For Stata

The section below takes the `valid_match_review_acc_260407_main.dta` generated above and rebuilds the final `core_simi_panel_260501.dta` used by `run_core_simi_explicit_regressions_260501.do`.

```{r core-simi-260501-final}
library(dplyr)
library(readr)
library(stringr)
library(tidyr)
library(haven)
library(purrr)
library(fixest)

if ("setFixest_notes" %in% getNamespaceExports("fixest")) {
  setFixest_notes(FALSE)
}
if ("setFixest_nthreads" %in% getNamespaceExports("fixest")) {
  setFixest_nthreads(1)
}

RUN_ID <- "260501"
PERM_REPS <- 200L

detect_project_dir <- function() {
  input <- tryCatch(knitr::current_input(), error = function(e) NULL)
  if (!is.null(input) && nzchar(input)) {
    input_dir <- dirname(normalizePath(input, winslash = "/", mustWork = FALSE))
    if (file.exists(file.path(input_dir, "valid_match_review_acc_260407_main.dta"))) {
      return(normalizePath(input_dir, winslash = "/", mustWork = TRUE))
    }
  }
  cwd <- normalizePath(getwd(), winslash = "/", mustWork = TRUE)
  if (file.exists(file.path(cwd, "valid_match_review_acc_260407_main.dta"))) return(cwd)
  stop("Cannot locate valid_match_review_acc_260407_main.dta. Run the first part of this Rmd first.")
}

assert_inside_project <- function(paths, project_dir) {
  root <- normalizePath(project_dir, winslash = "/", mustWork = TRUE)
  normalized <- normalizePath(paths, winslash = "/", mustWork = FALSE)
  outside <- normalized[!startsWith(normalized, paste0(root, "/")) & normalized != root]
  if (length(outside) > 0) {
    stop(paste("Refusing to write outside project root:", paste(outside, collapse = ", ")))
  }
  invisible(TRUE)
}

safe_median <- function(x) if (all(is.na(x))) NA_real_ else median(x, na.rm = TRUE)
safe_quantile <- function(x, p) if (all(is.na(x))) NA_real_ else as.numeric(quantile(x, p, na.rm = TRUE, names = FALSE))

extract_term <- function(model, pattern) {
  if (is.null(model)) {
    return(tibble(term = NA_character_, estimate = NA_real_, std_error = NA_real_, p_value = NA_real_))
  }
  ct <- as.data.frame(coeftable(model))
  ct$term <- rownames(ct)
  rownames(ct) <- NULL
  hit <- ct %>% filter(str_detect(term, pattern)) %>% slice(1)
  if (nrow(hit) == 0) {
    return(tibble(term = NA_character_, estimate = NA_real_, std_error = NA_real_, p_value = NA_real_))
  }
  tibble(
    term = hit$term[[1]],
    estimate = hit$Estimate[[1]],
    std_error = hit$`Std. Error`[[1]],
    p_value = hit$`Pr(>|t|)`[[1]]
  )
}

is_neg_sig <- function(term, alpha = 0.10) {
  isTRUE(!is.na(term$estimate) && !is.na(term$p_value) && term$estimate < 0 && term$p_value < alpha)
}

control_specs <- list(
  rich8_current = c(
    "ln_recent_volumn", "recent_sd", "ln_lag_volumn_acc",
    "lag_avg_rating_acc", "lag_sd_acc", "lag_avg_rating_month",
    "ln_avg_com_RevPAR", "ln_lag_RevPAR_clean"
  ),
  quality6 = c(
    "ln_recent_volumn", "ln_lag_volumn_acc", "lag_avg_rating_acc",
    "lag_avg_rating_month", "ln_avg_com_RevPAR", "review_freshness",
    "ln_lag_RevPAR_clean"
  ),
  base4_acc = c(
    "ln_recent_volumn", "ln_lag_volumn_acc", "lag_avg_rating_acc",
    "ln_avg_com_RevPAR", "ln_lag_RevPAR_clean"
  ),
  base4_month = c(
    "ln_recent_volumn", "ln_lag_volumn_acc", "lag_avg_rating_month",
    "ln_avg_com_RevPAR", "ln_lag_RevPAR_clean"
  ),
  lean3 = c(
    "ln_recent_volumn", "ln_lag_volumn_acc",
    "ln_avg_com_RevPAR", "ln_lag_RevPAR_clean"
  ),
  momentum_plus = c(
    "ln_recent_volumn", "ln_lag_volumn_acc", "lag_avg_rating_acc",
    "ln_avg_com_RevPAR", "rating_momentum", "volume_momentum",
    "review_freshness", "ln_lag_RevPAR_clean"
  )
)

dep_vars <- c("ln_RevPAR_clean", "ln_RevPAR_w199", "ln_RevPAR", "d_ln_RevPAR")
sample_names <- c("full", "pre2020", "exclude2020", "post2013", "post2013_excl2020", "focus50", "focus100", "star_observed")

sample_keep <- function(df, sample_name) {
  if (sample_name == "full") return(rep(TRUE, nrow(df)))
  if (sample_name == "pre2020") return(df$Year <= 2019)
  if (sample_name == "exclude2020") return(df$Year != 2020)
  if (sample_name == "post2013") return(df$Year >= 2013)
  if (sample_name == "post2013_excl2020") return(df$Year >= 2013 & df$Year != 2020)
  if (sample_name == "focus50") return(df$review_total_hotel >= 50)
  if (sample_name == "focus100") return(df$review_total_hotel >= 100)
  if (sample_name == "star_observed") return(!is.na(df$star_class))
  stop(paste("Unknown sample:", sample_name))
}

make_formula <- function(dep, controls, fe = TRUE, interaction = NULL) {
  rhs <- c("sim_mean", controls)
  if (!is.null(interaction)) {
    rhs <- c("sim_mean", interaction, paste0("sim_mean:", interaction), controls)
  }
  if (fe) {
    return(as.formula(paste(dep, "~", paste(rhs, collapse = " + "), "| HotelID + year_month")))
  }
  as.formula(paste(dep, "~", paste(rhs, collapse = " + ")))
}

rule_meta <- function(rule_id) {
  parts <- str_match(rule_id, "^(overall|ym|cityy|cityym)_(median|3070|4060)$")
  if (all(is.na(parts))) stop(paste("Unknown group rule:", rule_id))
  block_vars <- list(
    overall = character(0),
    ym = c("Year", "Mon"),
    cityy = c("CityID", "Year"),
    cityym = c("CityID", "Year", "Mon")
  )[[parts[[2]]]]
  list(scope = parts[[2]], boundary = parts[[3]], block_vars = block_vars)
}

group_cache <- new.env(parent = emptyenv())

build_group <- function(df, source_var, rule_id) {
  if (str_starts(rule_id, "star_")) {
    return(
      df %>%
        transmute(
          panel_row_id, HotelID, CityID, Year, Mon, year_month,
          group_flag = case_when(
            rule_id == "star_lt3_ge3" & !is.na(star_class) & star_class < 3 ~ 0L,
            rule_id == "star_lt3_ge3" & !is.na(star_class) & star_class >= 3 ~ 1L,
            rule_id == "star_le3_gt3" & !is.na(star_class) & star_class <= 3 ~ 0L,
            rule_id == "star_le3_gt3" & !is.na(star_class) & star_class > 3 ~ 1L,
            rule_id == "star_lt3_gt3" & !is.na(star_class) & star_class < 3 ~ 0L,
            rule_id == "star_lt3_gt3" & !is.na(star_class) & star_class > 3 ~ 1L,
            rule_id == "star_le35_gt35" & !is.na(star_class) & star_class <= 3.5 ~ 0L,
            rule_id == "star_le35_gt35" & !is.na(star_class) & star_class > 3.5 ~ 1L,
            rule_id == "star_le25_gt25" & !is.na(star_class) & star_class <= 2.5 ~ 0L,
            rule_id == "star_le25_gt25" & !is.na(star_class) & star_class > 2.5 ~ 1L,
            TRUE ~ NA_integer_
          ),
          block_id = as.character(CityID)
        )
    )
  }

  meta <- rule_meta(rule_id)
  tmp <- df %>% mutate(raw_value = .data[[source_var]])
  if (length(meta$block_vars) > 0) {
    tmp <- tmp %>% group_by(across(all_of(meta$block_vars)))
  }
  tmp <- tmp %>%
    mutate(
      block_obs = sum(!is.na(raw_value)),
      q30 = safe_quantile(raw_value, 0.30),
      q40 = safe_quantile(raw_value, 0.40),
      q60 = safe_quantile(raw_value, 0.60),
      q70 = safe_quantile(raw_value, 0.70),
      med = safe_median(raw_value),
      group_flag = case_when(
        is.na(raw_value) ~ NA_integer_,
        meta$boundary == "median" & block_obs >= 2 & raw_value < med ~ 0L,
        meta$boundary == "median" & block_obs >= 2 & raw_value >= med ~ 1L,
        meta$boundary == "3070" & block_obs >= 5 & raw_value <= q30 ~ 0L,
        meta$boundary == "3070" & block_obs >= 5 & raw_value >= q70 ~ 1L,
        meta$boundary == "4060" & block_obs >= 5 & raw_value <= q40 ~ 0L,
        meta$boundary == "4060" & block_obs >= 5 & raw_value >= q60 ~ 1L,
        TRUE ~ NA_integer_
      )
    ) %>%
    ungroup()

  block_id <- if (length(meta$block_vars) == 0) {
    rep("overall", nrow(tmp))
  } else {
    as.character(do.call(interaction, c(tmp[meta$block_vars], list(drop = TRUE, lex.order = TRUE))))
  }
  tmp %>%
    mutate(block_id = block_id) %>%
    transmute(panel_row_id, HotelID, CityID, Year, Mon, year_month, group_flag, block_id)
}

get_group <- function(base, sample_name, source_var, rule_id) {
  key <- paste(sample_name, source_var, rule_id, sep = "::")
  if (exists(key, envir = group_cache, inherits = FALSE)) {
    return(get(key, envir = group_cache, inherits = FALSE))
  }
  grp <- build_group(base, source_var, rule_id)
  assign(key, grp, envir = group_cache)
  grp
}

run_h1_spec <- function(df, sample, dep_var, control_family) {
  controls <- control_specs[[control_family]]
  req <- unique(c(dep_var, "sim_mean", controls, "HotelID", "year_month"))
  dat <- df %>%
    filter(sample_keep(., sample)) %>%
    filter(if_all(all_of(req), ~ !is.na(.x)))
  if (nrow(dat) < 800 || n_distinct(dat$HotelID) < 30) return(tibble())
  m_ols <- tryCatch(feols(make_formula(dep_var, controls, fe = FALSE), data = dat, cluster = ~HotelID), error = function(e) NULL)
  m_fe <- tryCatch(feols(make_formula(dep_var, controls, fe = TRUE), data = dat, cluster = ~HotelID), error = function(e) NULL)
  o <- extract_term(m_ols, "^sim_mean$")
  f <- extract_term(m_fe, "^sim_mean$")
  x_sd <- sd(dat$sim_mean, na.rm = TRUE)
  tibble(
    sample, dep_var, sim_var = "sim_mean", control_family,
    controls = paste(controls, collapse = " "),
    observations = nrow(dat), hotels = n_distinct(dat$HotelID), sim_sd = x_sd,
    ols_beta = o$estimate, ols_se = o$std_error, ols_p = o$p_value,
    fe_beta = f$estimate, fe_se = f$std_error, fe_p = f$p_value,
    ols_std_effect = o$estimate * x_sd,
    fe_std_effect = f$estimate * x_sd,
    h1_pass = as.integer(is_neg_sig(o, 0.05) && is_neg_sig(f, 0.05))
  )
}

screen_hetero_ols <- function(df, spec, model_spec, rule_id) {
  controls <- control_specs[[model_spec$control_family]]
  base <- df %>% filter(sample_keep(., model_spec$sample))
  grp <- get_group(base, model_spec$sample, spec$source_var, rule_id)
  dat <- base %>%
    left_join(grp %>% select(panel_row_id, group_flag, block_id), by = "panel_row_id") %>%
    filter(!is.na(group_flag))
  req <- unique(c(model_spec$dep_var, "sim_mean", controls, "HotelID", "year_month", "group_flag"))
  dat <- dat %>% filter(if_all(all_of(req), ~ !is.na(.x)))
  if (nrow(dat) < 800 || n_distinct(dat$group_flag) < 2 || min(table(dat$group_flag)) < 250) return(tibble())
  if (min(n_distinct(dat$HotelID[dat$group_flag == 0]), n_distinct(dat$HotelID[dat$group_flag == 1])) < 10) return(tibble())
  # Fast screen only. Clustered SEs are used in FE refinement and final Stata tables.
  m <- tryCatch(feols(make_formula(model_spec$dep_var, controls, fe = FALSE, interaction = "group_flag"), data = dat), error = function(e) NULL)
  main <- extract_term(m, "^sim_mean$")
  diff <- extract_term(m, "sim_mean:group_flag|group_flag:sim_mean")
  beta_low <- main$estimate
  beta_high <- main$estimate + diff$estimate
  direction_ok <- isTRUE(if (spec$expected == "low_stronger") beta_low < beta_high else beta_high < beta_low)
  tibble(
    hypothesis = spec$hypothesis, moderator = spec$moderator, sample = model_spec$sample,
    dep_var = model_spec$dep_var, sim_var = "sim_mean", control_family = model_spec$control_family,
    controls = paste(controls, collapse = " "),
    source_var = spec$source_var, group_rule = rule_id, expected = spec$expected,
    observations = nrow(dat), hotels = n_distinct(dat$HotelID),
    n_low = sum(dat$group_flag == 0), n_high = sum(dat$group_flag == 1),
    hotel_low = n_distinct(dat$HotelID[dat$group_flag == 0]),
    hotel_high = n_distinct(dat$HotelID[dat$group_flag == 1]),
    beta_low_screen = beta_low, beta_high_screen = beta_high,
    beta_diff_screen = diff$estimate, p_diff_screen = diff$p_value,
    direction_screen = as.integer(direction_ok)
  )
}

evaluate_hetero_fe <- function(df, row) {
  controls <- control_specs[[row$control_family]]
  base <- df %>% filter(sample_keep(., row$sample))
  grp <- get_group(base, row$sample, row$source_var, row$group_rule)
  dat <- base %>%
    left_join(grp %>% select(panel_row_id, group_flag, block_id), by = "panel_row_id") %>%
    filter(!is.na(group_flag))
  req <- unique(c(row$dep_var, "sim_mean", controls, "HotelID", "year_month", "group_flag"))
  dat <- dat %>% filter(if_all(all_of(req), ~ !is.na(.x)))
  empty <- tibble(
    hypothesis = row$hypothesis, moderator = row$moderator, sample = row$sample,
    dep_var = row$dep_var, sim_var = "sim_mean", control_family = row$control_family,
    controls = paste(controls, collapse = " "),
    source_var = row$source_var, group_rule = row$group_rule, expected = row$expected,
    observations = nrow(dat), hotels = n_distinct(dat$HotelID),
    n_low = sum(dat$group_flag == 0, na.rm = TRUE), n_high = sum(dat$group_flag == 1, na.rm = TRUE),
    hotel_low = n_distinct(dat$HotelID[dat$group_flag == 0]),
    hotel_high = n_distinct(dat$HotelID[dat$group_flag == 1]),
    beta_low = NA_real_, se_low = NA_real_, p_low = NA_real_,
    beta_high = NA_real_, se_high = NA_real_, p_high = NA_real_,
    beta_diff = NA_real_, p_interaction = NA_real_,
    direction_ok = 0L, expected_group_sig = 0L, diff_sig = 0L, pass = 0L
  )
  if (nrow(dat) < 800 || n_distinct(dat$group_flag) < 2 || min(table(dat$group_flag)) < 250) return(empty)
  if (min(n_distinct(dat$HotelID[dat$group_flag == 0]), n_distinct(dat$HotelID[dat$group_flag == 1])) < 10) return(empty)
  f <- make_formula(row$dep_var, controls, fe = TRUE)
  fi <- make_formula(row$dep_var, controls, fe = TRUE, interaction = "group_flag")
  low_m <- tryCatch(feols(f, data = dat %>% filter(group_flag == 0), cluster = ~HotelID), error = function(e) NULL)
  high_m <- tryCatch(feols(f, data = dat %>% filter(group_flag == 1), cluster = ~HotelID), error = function(e) NULL)
  int_m <- tryCatch(feols(fi, data = dat, cluster = ~HotelID), error = function(e) NULL)
  low <- extract_term(low_m, "^sim_mean$")
  high <- extract_term(high_m, "^sim_mean$")
  diff <- extract_term(int_m, "sim_mean:group_flag|group_flag:sim_mean")
  direction_val <- isTRUE(if (row$expected == "low_stronger") low$estimate < high$estimate else high$estimate < low$estimate)
  expected_sig_val <- if (row$expected == "low_stronger") is_neg_sig(low, 0.10) else is_neg_sig(high, 0.10)
  diff_sig_val <- isTRUE(!is.na(diff$p_value) && diff$p_value < 0.10)
  empty %>%
    mutate(
      beta_low = low$estimate, se_low = low$std_error, p_low = low$p_value,
      beta_high = high$estimate, se_high = high$std_error, p_high = high$p_value,
      beta_diff = diff$estimate, p_interaction = diff$p_value,
      direction_ok = as.integer(direction_val),
      expected_group_sig = as.integer(expected_sig_val),
      diff_sig = as.integer(diff_sig_val),
      pass = as.integer(direction_val && expected_sig_val && diff_sig_val)
    )
}

run_perm <- function(df, row) {
  controls <- control_specs[[row$control_family]]
  base <- df %>% filter(sample_keep(., row$sample))
  grp <- get_group(base, row$sample, row$source_var, row$group_rule)
  dat <- base %>%
    left_join(grp %>% select(panel_row_id, group_flag, block_id), by = "panel_row_id") %>%
    filter(!is.na(group_flag))
  req <- unique(c(row$dep_var, "sim_mean", controls, "HotelID", "year_month", "group_flag"))
  dat <- dat %>% filter(if_all(all_of(req), ~ !is.na(.x)))
  if (nrow(dat) < 800 || is.na(row$beta_diff)) return(tibble(p_perm = NA_real_, reps = 0L))
  observed <- abs(row$beta_diff)
  f <- make_formula(row$dep_var, controls, fe = TRUE, interaction = "group_perm")
  set.seed(260501)
  if (str_starts(row$group_rule, "star_")) {
    hotel_grp <- dat %>% distinct(HotelID, CityID, group_flag)
    blocks <- split(seq_len(nrow(hotel_grp)), hotel_grp$CityID)
    draw <- function() {
      g <- hotel_grp$group_flag
      for (idx in blocks) if (length(idx) > 1) g[idx] <- sample(g[idx], length(idx))
      g[match(dat$HotelID, hotel_grp$HotelID)]
    }
  } else {
    blocks <- split(seq_len(nrow(dat)), dat$block_id)
    draw <- function() {
      g <- dat$group_flag
      for (idx in blocks) if (length(idx) > 1) g[idx] <- sample(g[idx], length(idx))
      g
    }
  }
  stats <- vapply(seq_len(PERM_REPS), function(i) {
    m <- tryCatch(
      suppressWarnings(feols(f, data = dat %>% mutate(group_perm = draw()), cluster = ~HotelID)),
      error = function(e) NULL
    )
    term <- extract_term(m, "sim_mean:group_perm|group_perm:sim_mean")
    abs(term$estimate)
  }, numeric(1))
  tibble(p_perm = mean(stats >= observed, na.rm = TRUE), reps = PERM_REPS)
}

project_dir <- detect_project_dir()
out_root <- project_dir
dirs <- file.path(out_root, c("csv", "scans", "tables", "logs"))
assert_inside_project(c(out_root, dirs), project_dir)
walk(c(out_root, dirs), ~ dir.create(.x, recursive = TRUE, showWarnings = FALSE))

input_panel <- file.path(project_dir, "valid_match_review_acc_260407_main.dta")
panel <- read_dta(input_panel)
if (!"panel_row_id" %in% names(panel)) panel <- panel %>% mutate(panel_row_id = row_number())

required_vars <- unique(c(
  "HotelID", "CityID", "Zip", "Year", "Mon", "year_month", "review_total_hotel",
  "sim_mean", dep_vars, unlist(control_specs, use.names = FALSE),
  "lag_avg_rating_month", "lag_avg_rating_acc", "rating_last_5", "lag_rating_last_5",
  "lag_recent_volumn", "recent_volumn", "lag_volumn_acc", "volumn_acc",
  "star_class", "ln_lag_avg_com_RevPAR"
))
missing_vars <- setdiff(required_vars, names(panel))
if (length(missing_vars) > 0) {
  stop(paste("Missing required variables:", paste(missing_vars, collapse = ", ")))
}

panel <- panel %>%
  arrange(HotelID, Year, Mon) %>%
  mutate(
    rating_recent_gap = lag_avg_rating_month - lag_avg_rating_acc,
    price_gap = ln_lag_RevPAR_clean - ln_lag_avg_com_RevPAR,
    cs_sample_full = 1L,
    cs_sample_pre2020 = as.integer(Year <= 2019),
    cs_sample_exclude2020 = as.integer(Year != 2020),
    cs_sample_post2013 = as.integer(Year >= 2013),
    cs_sample_post2013_excl2020 = as.integer(Year >= 2013 & Year != 2020),
    cs_sample_focus50 = as.integer(review_total_hotel >= 50),
    cs_sample_focus100 = as.integer(review_total_hotel >= 100),
    cs_sample_star_observed = as.integer(!is.na(star_class))
  ) %>%
  group_by(CityID) %>%
  mutate(star_dm_city = star_class - mean(star_class, na.rm = TRUE)) %>%
  ungroup()

sample_audit <- tibble(sample = sample_names) %>%
  mutate(
    observations = map_int(sample, ~ sum(sample_keep(panel, .x), na.rm = TRUE)),
    hotels = map_int(sample, ~ n_distinct(panel$HotelID[sample_keep(panel, .x)])),
    min_year = map_int(sample, ~ min(panel$Year[sample_keep(panel, .x)], na.rm = TRUE)),
    max_year = map_int(sample, ~ max(panel$Year[sample_keep(panel, .x)], na.rm = TRUE)),
    star_nonmissing = map_int(sample, ~ sum(sample_keep(panel, .x) & !is.na(panel$star_class), na.rm = TRUE)),
    star_coverage = star_nonmissing / observations
  )

message("Running core-simi H1 OLS/FE scan...")
h1_grid <- crossing(sample = sample_names, dep_var = dep_vars, control_family = names(control_specs))
h1_scan <- pmap_dfr(h1_grid, ~ run_h1_spec(panel, ..1, ..2, ..3))

h1_selected <- h1_scan %>%
  mutate(
    dep_rank = match(dep_var, dep_vars),
    sample_rank = match(sample, sample_names),
    control_rank = match(control_family, names(control_specs)),
    score = h1_pass * 1000 + abs(fe_std_effect) * 100 - coalesce(fe_p, 1) - coalesce(ols_p, 1)
  ) %>%
  arrange(desc(score), dep_rank, sample_rank, control_rank) %>%
  slice(1)

h1_gmm_candidates <- h1_scan %>%
  filter(h1_pass == 1) %>%
  mutate(
    dep_rank = match(dep_var, dep_vars),
    sample_rank = match(sample, sample_names),
    control_rank = match(control_family, names(control_specs)),
    gmm_rank = abs(fe_std_effect) * 100 - coalesce(fe_p, 1) - coalesce(ols_p, 1)
  ) %>%
  arrange(dep_rank, sample_rank, control_rank, desc(gmm_rank)) %>%
  distinct(sample, dep_var, control_family, .keep_all = TRUE) %>%
  slice_head(n = 30)

numeric_rules <- c(
  "overall_median", "ym_median", "cityy_median", "cityym_median",
  "ym_3070", "cityy_3070", "ym_4060", "cityy_4060"
)
star_rules <- c("star_lt3_ge3", "star_le3_gt3", "star_lt3_gt3", "star_le35_gt35", "star_le25_gt25")

moderators <- tibble(
  hypothesis = c(
    rep("h2", 6),
    rep("h3", 7),
    rep("h4", 5)
  ),
  moderator = c(
    "rating_month", "rating_acc", "rating_last5", "rating_lag_last5", "rating_momentum", "rating_gap",
    "volume_lag_recent", "volume_recent", "volume_lag_acc", "volume_acc", "volume_momentum", "volume_ln_recent", "volume_ln_acc",
    "star_class", "star_dm_city", "highend_lag_revpar", "highend_compete_revpar", "highend_price_gap"
  ),
  source_var = c(
    "lag_avg_rating_month", "lag_avg_rating_acc", "rating_last_5", "lag_rating_last_5", "rating_momentum", "rating_recent_gap",
    "lag_recent_volumn", "recent_volumn", "lag_volumn_acc", "volumn_acc", "volume_momentum", "ln_recent_volumn", "ln_lag_volumn_acc",
    "star_class", "star_dm_city", "ln_lag_RevPAR_clean", "ln_lag_avg_com_RevPAR", "price_gap"
  ),
  expected = c(rep("low_stronger", 6), rep("high_stronger", 12))
)

hetero_model_specs <- h1_scan %>%
  filter(!is.na(fe_p), !is.na(ols_p)) %>%
  mutate(model_rank = h1_pass * 1000 + abs(fe_std_effect) * 100 - coalesce(fe_p, 1) - coalesce(ols_p, 1)) %>%
  arrange(desc(model_rank), match(dep_var, dep_vars), match(sample, sample_names)) %>%
  distinct(sample, dep_var, control_family) %>%
  slice_head(n = 16)

hetero_grid <- moderators %>%
  mutate(
    group_rule = pmap(
      list(hypothesis, source_var),
      function(hypothesis, source_var) {
        if (hypothesis == "h4" && source_var == "star_class") {
          c(star_rules, "overall_median", "overall_3070", "overall_4060", "cityy_median", "ym_median")
        } else if (hypothesis == "h4") {
          c("ym_median", "cityy_median", "ym_3070", "cityy_3070", "ym_4060", "cityy_4060")
        } else {
          numeric_rules
        }
      }
    )
  ) %>%
  unnest(group_rule) %>%
  crossing(hetero_model_specs)

message("Running core-simi H2-H4 OLS interaction screen...")
hetero_screen <- pmap_dfr(
  hetero_grid,
  function(hypothesis, moderator, source_var, expected, group_rule,
           sample, dep_var, sim_var, control_family, controls, observations,
           hotels, sim_sd, ols_beta, ols_se, ols_p, fe_beta, fe_se, fe_p,
           ols_std_effect, fe_std_effect, h1_pass, model_rank) {
    screen_hetero_ols(
      panel,
      list(hypothesis = hypothesis, moderator = moderator, source_var = source_var, expected = expected),
      list(sample = sample, dep_var = dep_var, control_family = control_family),
      group_rule
    )
  }
)

message("Running core-simi H2-H4 FE refinement...")
hetero_refine_input <- hetero_screen %>%
  filter(!is.na(p_diff_screen)) %>%
  group_by(hypothesis) %>%
  arrange(desc(direction_screen), p_diff_screen, desc(hotels), desc(observations), .by_group = TRUE) %>%
  slice_head(n = 70) %>%
  ungroup()

hetero_scan <- pmap_dfr(hetero_refine_input, function(...) evaluate_hetero_fe(panel, list(...)))

message("Running permutation checks for selected core-simi heterogeneity candidates...")
perm_input <- hetero_scan %>%
  filter(!is.na(p_interaction)) %>%
  group_by(hypothesis) %>%
  arrange(desc(pass), desc(direction_ok), desc(expected_group_sig), p_interaction, desc(hotel_low + hotel_high), .by_group = TRUE) %>%
  slice_head(n = 5) %>%
  ungroup()

perm_scan <- perm_input %>%
  mutate(row_id = row_number()) %>%
  split(.$row_id) %>%
  map_dfr(function(row_df) {
    perm <- run_perm(panel, row_df[1, ])
    bind_cols(row_df %>% select(-row_id), perm)
  }) %>%
  mutate(
    diff_sig = as.integer((!is.na(p_interaction) & p_interaction < 0.10) | (!is.na(p_perm) & p_perm < 0.10)),
    pass = as.integer(direction_ok == 1 & expected_group_sig == 1 & diff_sig == 1)
  )

selected_hetero <- perm_scan %>%
  group_by(hypothesis) %>%
  arrange(desc(pass), desc(direction_ok), desc(expected_group_sig), p_interaction, p_perm, desc(hotel_low + hotel_high), .by_group = TRUE) %>%
  slice(1) %>%
  ungroup()

for (hyp in c("h2", "h3", "h4")) {
  row <- selected_hetero %>% filter(hypothesis == hyp) %>% slice(1)
  var_name <- paste0("cs_group_", hyp)
  panel[[var_name]] <- NA_integer_
  if (nrow(row) == 1) {
    base <- panel %>% filter(sample_keep(., row$sample))
    grp <- get_group(base, row$sample, row$source_var, row$group_rule)
    panel[[var_name]][match(grp$panel_row_id, panel$panel_row_id)] <- grp$group_flag
  }
}

variable_dictionary <- tibble(
  variable = c("sim_mean", dep_vars, names(control_specs), unlist(control_specs, use.names = FALSE), moderators$source_var),
  role = c(
    "fixed_similarity",
    rep("dependent_candidate", length(dep_vars)),
    rep("control_family", length(control_specs)),
    rep("control_variable", length(unlist(control_specs, use.names = FALSE))),
    rep("moderator_candidate", nrow(moderators))
  )
) %>%
  distinct(variable, role)

paths <- c(
  file.path(out_root, paste0("core_simi_panel_", RUN_ID, ".dta")),
  file.path(out_root, "csv", paste0("sample_audit_", RUN_ID, ".csv")),
  file.path(out_root, "csv", paste0("h1_selected_", RUN_ID, ".csv")),
  file.path(out_root, "csv", paste0("h1_gmm_candidates_", RUN_ID, ".csv")),
  file.path(out_root, "csv", paste0("heterogeneity_selected_", RUN_ID, ".csv")),
  file.path(out_root, "csv", paste0("variable_dictionary_", RUN_ID, ".csv")),
  file.path(out_root, "scans", paste0("h1_ols_fe_scan_", RUN_ID, ".csv")),
  file.path(out_root, "scans", paste0("heterogeneity_ols_screen_", RUN_ID, ".csv")),
  file.path(out_root, "scans", paste0("heterogeneity_fe_scan_", RUN_ID, ".csv")),
  file.path(out_root, "scans", paste0("heterogeneity_perm_scan_", RUN_ID, ".csv"))
)
assert_inside_project(paths, project_dir)

write_dta(panel, paths[[1]], version = 14)
write_csv(sample_audit, paths[[2]])
write_csv(h1_selected, paths[[3]])
write_csv(h1_gmm_candidates, paths[[4]])
write_csv(selected_hetero, paths[[5]])
write_csv(variable_dictionary, paths[[6]])
write_csv(h1_scan, paths[[7]])
write_csv(hetero_screen, paths[[8]])
write_csv(hetero_scan, paths[[9]])
write_csv(perm_scan, paths[[10]])

message("Wrote core-simi outputs under: ", out_root)

```

## 9. Alternative RRS Scopes 5/10/15/20/30

This section builds robustness versions of review similarity using alternative recent-review scopes. For each hotel-month and each scope `N` in `5, 10, 15, 20, 30`, the review set is defined as the most recent `N` reviews before the month starts plus all reviews posted during the month. The script computes pairwise cosine similarity from the same Doc2Vec 200-dimensional vectors, and recomputes the scope-specific `recent_volumn_N`, `ln_recent_volumn_N`, `recent_sd_N`, and `recent_rating_N`.

The implementation is checkpointed by hotel batches to avoid keeping large nested review matrices in memory. If the run stops, rerunning the chunk skips existing checkpoint files and resumes from the remaining batches.

```{r alternative-rrs-scopes-260509, eval=FALSE}
source(file.path(project_dir, "scripts/r/build_scope_ars_260509.R"))
```
